---
title: "03: Chronic Dermatology Cohort - Basic Descriptive Statistics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

### Load Libraries and Data

```{r}
library(data.table)
library(dplyr)
library(gt)
library(stringr)

# Enhanced p-value formatting for standardized reporting
format_pvalue <- function(p) {
  if (is.na(p)) return("—")
  if (p < 0.001) return("<0.001")
  if (p < 0.01) return(sprintf("%.3f", p))
  if (p < 0.05) return(sprintf("%.3f", p))
  return(sprintf("%.2f", p))
}

data_path <- "Z:/Kucirek/"

# Load MASTER datasets from File 01 - SINGLE SOURCE OF TRUTH
chronic_derm_master <- readRDS(file.path(data_path, "chronic_derm_master.rds"))
chronic_derm_patient_summary <- readRDS(file.path(data_path, "chronic_derm_patient_summary.rds"))
chronic_derm_patient_conditions <- readRDS(file.path(data_path, "chronic_derm_patient_conditions.rds"))
condition_patient_counts <- readRDS(file.path(data_path, "condition_patient_counts.rds"))
condition_column_mapping <- readRDS(file.path(data_path, "condition_column_mapping.rds"))
result_info <- readRDS(file.path(data_path, "result_info.rds"))

# Load legacy files for compatibility (but use master datasets for analysis)
result_wide <- readRDS(file.path(data_path, "result_wide.rds"))
chronic_derm_cohort <- readRDS(file.path(data_path, "chronic_derm_cohort.rds"))

setDT(chronic_derm_master)
setDT(chronic_derm_patient_summary)
setDT(result_wide)
setDT(chronic_derm_cohort)
setDT(result_info)

# Check that required PHQ columns from File 01 exist
required_cols <- c("phq_score", "phq_clinical", "phq_subclinical", "phq_type_used")
missing_cols <- setdiff(required_cols, names(result_wide))

if (length(missing_cols) > 0) {
  stop(paste("ERROR: Required PHQ columns missing from File 01:", 
             paste(missing_cols, collapse = ", "), 
             "\nPlease re-run '01_joining_and_cohort_definition.Rmd' first."))
}

cat("=== BASIC CHRONIC DERMATOLOGY COHORT ANALYSIS ===\n")

# MASTER DATASET VERIFICATION
if (!exists("chronic_derm_master") || nrow(chronic_derm_master) == 0) {
  stop("ERROR: chronic_derm_master not loaded properly. Run File 01 first!")
}
if (!exists("chronic_derm_patient_summary") || nrow(chronic_derm_patient_summary) == 0) {
  stop("ERROR: chronic_derm_patient_summary not loaded properly. Run File 01 first!")
}

cat("Master datasets loaded successfully:\n")
cat("  chronic_derm_master: ", nrow(chronic_derm_master), " encounters\n")
cat("  chronic_derm_patient_summary: ", nrow(chronic_derm_patient_summary), " patients\n")
cat("  condition_patient_counts available: ", length(condition_patient_counts), " conditions\n")

# Verify condition columns exist
condition_cols <- grep("^condition_", names(chronic_derm_patient_summary), value = TRUE)
cat("  Pre-assigned condition columns: ", length(condition_cols), "\n")
cat("    ", paste(condition_cols, collapse = ", "), "\n")
```

## 1. Cohort Overview - Using Master Datasets

```{r}
cat("\n=== 1. CHRONIC DERMATOLOGY COHORT OVERVIEW (MASTER DATASETS) ===\n")

# VERIFICATION: Compare master vs legacy counts
chronic_derm_patient_ids <- unique(chronic_derm_patient_summary$mrn_deid)
legacy_patient_ids <- unique(chronic_derm_cohort$mrn_deid)

cat("VERIFICATION:\n")
cat("  Master dataset patients:", length(chronic_derm_patient_ids), "\n")
cat("  Legacy dataset patients:", length(legacy_patient_ids), "\n")
cat("  Difference:", length(chronic_derm_patient_ids) - length(legacy_patient_ids), "\n")

# Use MASTER datasets for all analysis
chronic_derm_encounters <- chronic_derm_master  # Pre-filtered and standardized
chronic_derm_phq_status <- chronic_derm_patient_summary  # Pre-calculated patient summaries

cat("\nMASTER DATASET SUMMARY:\n")
cat("Chronic derm patients:", nrow(chronic_derm_phq_status), "\n")
cat("Total encounters for chronic derm patients:", nrow(chronic_derm_encounters), "\n")

# Basic PHQ statistics
cat("\n=== PHQ SCREENING RESULTS ===\n")
cat("Patients with clinical depression (10+):", sum(chronic_derm_phq_status$ever_clinical), 
    " (", round(mean(chronic_derm_phq_status$ever_clinical) * 100, 1), "%)\n")
cat("Patients with subclinical depression (5-9):", sum(chronic_derm_phq_status$ever_subclinical), 
    " (", round(mean(chronic_derm_phq_status$ever_subclinical) * 100, 1), "%)\n")
cat("Patients with PHQ data:", sum(chronic_derm_phq_status$phq_encounters > 0), 
    " (", round(mean(chronic_derm_phq_status$phq_encounters > 0) * 100, 1), "%)\n")

# Clinical/Subclinical distribution
depression_summary <- chronic_derm_phq_status[, .(
  clinical_n = sum(ever_clinical),
  subclinical_n = sum(ever_subclinical),
  no_depression_n = sum(!ever_clinical & !ever_subclinical & phq_encounters > 0),
  no_data_n = sum(phq_encounters == 0)
)]
depression_summary[, `:=`(
  clinical_pct = round(clinical_n/nrow(chronic_derm_phq_status)*100, 1),
  subclinical_pct = round(subclinical_n/nrow(chronic_derm_phq_status)*100, 1),
  no_depression_pct = round(no_depression_n/nrow(chronic_derm_phq_status)*100, 1),
  no_data_pct = round(no_data_n/nrow(chronic_derm_phq_status)*100, 1)
)]
cat("\nDepression Classification (Patient-level):\n")
print(depression_summary)
```

## 2. Demographic Summary

```{r}
cat("\n=== 2. DEMOGRAPHIC SUMMARY ===\n")

# Merge with demographics from result_info (created in File 2)
chronic_derm_demographics <- merge(chronic_derm_phq_status, 
                                 result_info, 
                                 by = "mrn_deid")

# Simple demographic breakdown
demo_summary <- chronic_derm_demographics[, .(
  total_patients = .N,
  clinical_patients = sum(ever_clinical, na.rm = TRUE),
  clinical_rate = round(mean(ever_clinical, na.rm = TRUE) * 100, 1),
  subclinical_patients = sum(ever_subclinical, na.rm = TRUE),
  subclinical_rate = round(mean(ever_subclinical, na.rm = TRUE) * 100, 1)
)]

cat("Overall Summary:\n")
print(demo_summary)

# Basic demographic table
demo_table <- demo_summary %>%
  gt() %>%
  tab_header(
    title = "Chronic Dermatology Cohort Summary",
    subtitle = "Clinical and subclinical depression outcomes"
  ) %>%
  cols_label(
    total_patients = "Total Patients",
    clinical_patients = "Clinical Depression (10+)",
    clinical_rate = "Clinical Rate (%)",
    subclinical_patients = "Subclinical Depression (5-9)", 
    subclinical_rate = "Subclinical Rate (%)"
  ) %>%
  tab_options(
    table.border.top.color = "#495057",
    table.border.top.width = px(3),
    table.border.bottom.color = "#495057",
    table.border.bottom.width = px(2),
    column_labels.font.weight = "bold",
    column_labels.font.size = px(13),
    table.font.size = px(13),
    table.font.names = c("Arial", "Calibri", "Segoe UI", "sans-serif")
  )

print(demo_table)

# Save as CSV
csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
write.csv(demo_summary, file.path(csv_dir, "Chronic_Derm_Cohort_Summary.csv"), row.names = FALSE)
```

## 3. Condition-Specific Summary - Using Master Condition Assignments

```{r}
cat("\n=== 3. CONDITION-SPECIFIC SUMMARY (MASTER CONDITIONS) ===\n")

# NO MORE CONDITION REDEFINITION - Use master assignments from File 01
cat("Using pre-assigned conditions from File 01 master datasets\n")
cat("Verified condition counts from File 01:\n")
print(condition_patient_counts)

# Create condition summary using MASTER condition assignments
condition_summary_list <- list()
condition_names <- names(chronic_derm_patient_conditions)

for(condition_name in condition_names) {
  # Use the same column name mapping as File 01
  condition_col_name <- condition_column_mapping[[condition_name]]
  
  # Get patients with this condition from master dataset
  condition_patients <- chronic_derm_patient_conditions[[condition_name]]
  condition_phq_data <- chronic_derm_phq_status[mrn_deid %in% condition_patients]
  
  condition_summary_list[[condition_name]] <- data.table(
    condition_type = condition_name,
    total_patients = length(condition_patients),  # From master count
    clinical_patients = sum(condition_phq_data$ever_clinical, na.rm = TRUE),
    clinical_rate = round(mean(condition_phq_data$ever_clinical, na.rm = TRUE) * 100, 1),
    subclinical_patients = sum(condition_phq_data$ever_subclinical, na.rm = TRUE),
    subclinical_rate = round(mean(condition_phq_data$ever_subclinical, na.rm = TRUE) * 100, 1)
  )
}
condition_summary <- rbindlist(condition_summary_list)[order(-total_patients)]

cat("\nCONDITION VERIFICATION - Master vs Current:\n")
for(i in 1:nrow(condition_summary)) {
  condition_name <- condition_summary$condition_type[i]
  master_count <- condition_patient_counts[[condition_name]]
  current_count <- condition_summary$total_patients[i]
  status <- if(master_count == current_count) "✓" else "✗"
  cat(paste0("  ", condition_name, ": Master=", master_count, ", Current=", current_count, " ", status, "\n"))
}

cat("\nCondition-specific results:\n")
print(condition_summary)

# ===== FINAL VERIFICATION SYSTEM =====
cat("\n=== FILE 03 FINAL VERIFICATION ===\n")
verify_file03_consistency <- function() {
  cat("ACNE COUNT VERIFICATION:\n")
  
  # Method 1: Master count
  master_acne_count <- condition_patient_counts[["Acne"]]
  cat("  Master dataset (File 01): ", master_acne_count, " patients\n")
  
  # Method 2: Current condition summary
  current_acne_count <- condition_summary[condition_type == "Acne", total_patients]
  cat("  Current summary (File 03): ", current_acne_count, " patients\n")
  
  # Method 3: Direct count from patient conditions
  direct_acne_count <- length(chronic_derm_patient_conditions[["Acne"]])
  cat("  Direct from patient conditions: ", direct_acne_count, " patients\n")
  
  # Check consistency
  if(master_acne_count == current_acne_count && current_acne_count == direct_acne_count) {
    cat("  ✅ ALL COUNTS MATCH - CONSISTENCY ACHIEVED!\n")
  } else {
    cat("  ❌ COUNTS DO NOT MATCH - INVESTIGATE DISCREPANCY\n")
  }
  
  cat("\nALL CONDITIONS VERIFICATION:\n")
  for(condition_name in names(condition_patient_counts)) {
    master_count <- condition_patient_counts[[condition_name]]
    current_count <- condition_summary[condition_type == condition_name, total_patients]
    if(length(current_count) == 0) current_count <- 0
    status <- if(master_count == current_count) "✅" else "❌"
    cat(paste0("  ", condition_name, ": Master=", master_count, ", Current=", current_count, " ", status, "\n"))
  }
}
verify_file03_consistency()

# Simple condition table
condition_table <- condition_summary %>%
  gt() %>%
  tab_header(
    title = "Table 1. Depression Rates by Dermatologic Condition",
    subtitle = "Clinical and subclinical depression outcomes"
  ) %>%
  cols_label(
    condition_type = "Condition",
    total_patients = "Total Patients",
    clinical_patients = "Clinical (n)",
    clinical_rate = "Clinical (%)",
    subclinical_patients = "Subclinical (n)",
    subclinical_rate = "Subclinical (%)"
  ) %>%
  tab_options(
    table.border.top.color = "#495057",
    table.border.top.width = px(3),
    table.border.bottom.color = "#495057",
    table.border.bottom.width = px(2),
    column_labels.font.weight = "bold",
    column_labels.font.size = px(13),
    table.font.size = px(13),
    table.font.names = c("Arial", "Calibri", "Segoe UI", "sans-serif")
  )

print(condition_table)

# Save as CSV
csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
write.csv(condition_summary, file.path(csv_dir, "Table_1_Depression_Rates_by_Condition.csv"), row.names = FALSE)
```

## Summary

```{r}
cat("\n=== ANALYSIS SUMMARY ===\n")
cat("Basic descriptive analysis completed for chronic dermatology cohort\n")
cat("Total patients analyzed:", nrow(chronic_derm_phq_status), "\n")
cat("Conditions analyzed:", nrow(condition_summary), "\n")
cat("Analysis uses clinical (10+) and subclinical (5-9) depression thresholds from File 01\n")
```

## ADDITIONAL COMPARATIVE TABLES

### Clinical Depression Analysis (PHQ ≥10)

#### Table 1A: Clinical Depression - Pairwise Comparisons Between Demographic Levels

```{r}
# Pairwise comparisons of clinical depression rates between levels within each demographic variable  
# Use MASTER patient summary - already guaranteed to have PHQ data
chronic_derm_demographics_extended <- merge(chronic_derm_phq_status, 
                                          result_info, 
                                          by = "mrn_deid")
# Use patients who have both PHQ data AND complete demographics (consistent with File 2)
chronic_derm_with_phq <- chronic_derm_demographics_extended[phq_encounters > 0 & 
                                                           !is.na(age_at_encounter) & !is.na(sex) & 
                                                           !is.na(race_refined) & !is.na(ethnic_refined) & 
                                                           !is.na(fin_class)]

if(nrow(chronic_derm_with_phq) > 20) {
  clinical_pairwise_results <- list()
  total_n <- nrow(chronic_derm_with_phq)
  
  # Sex pairwise comparisons
  sex_levels <- chronic_derm_with_phq[!is.na(sex) & sex != "", 
                                     .(n = .N, clinical_n = sum(ever_clinical), clinical_rate = round(mean(ever_clinical)*100,1)), 
                                     by = sex]
  
  # Only include sex categories with ≥5% of total cohort
  sex_levels <- sex_levels[n >= total_n * 0.05]
  
  if(nrow(sex_levels) >= 2) {
    sex_list <- sex_levels$sex
    for(i in 1:(length(sex_list)-1)) {
      for(j in (i+1):length(sex_list)) {
        sex1 <- sex_list[i]
        sex2 <- sex_list[j]
        
        sex1_data <- chronic_derm_with_phq[sex == sex1]
        sex2_data <- chronic_derm_with_phq[sex == sex2]
        
        if(nrow(sex1_data) >= 10 && nrow(sex2_data) >= 10) {
          sex1_clinical <- sum(sex1_data$ever_clinical)
          sex1_total <- nrow(sex1_data)
          sex2_clinical <- sum(sex2_data$ever_clinical)
          sex2_total <- nrow(sex2_data)
          
          test_matrix <- matrix(c(sex1_clinical, sex1_total - sex1_clinical,
                                sex2_clinical, sex2_total - sex2_clinical), nrow = 2)
          fisher_test <- fisher.test(test_matrix)
          
          if(fisher_test$p.value < 0.05) {
            sex1_rate <- round(sex1_clinical/sex1_total*100, 1)
            sex2_rate <- round(sex2_clinical/sex2_total*100, 1)
            
            # Calculate OR and 95% CI
            odds_ratio <- fisher_test$estimate
            ci_lower <- fisher_test$conf.int[1]
            ci_upper <- fisher_test$conf.int[2]
            or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
            
            clinical_pairwise_results[[paste("Sex", sex1, "vs", sex2)]] <- list(
              Comparison = paste(sex1, "vs", sex2),
              Group1 = paste0(sex1, ": ", sex1_clinical, "/", sex1_total, " (", sex1_rate, "%)"),
              Group2 = paste0(sex2, ": ", sex2_clinical, "/", sex2_total, " (", sex2_rate, "%)"),
              OR_CI = or_ci,
              P_Value = format_pvalue(fisher_test$p.value),
              Variable = "Sex"
            )
          }
        }
      }
    }
  }
  
  # Age group comparisons (above vs below 65)
  chronic_derm_with_phq[, age_group := ifelse(age_at_encounter >= 65, "65+", "<65")]
  age_levels <- chronic_derm_with_phq[!is.na(age_group), 
                                     .(n = .N, clinical_n = sum(ever_clinical), clinical_rate = round(mean(ever_clinical)*100,1)), 
                                     by = age_group]
  
  if(nrow(age_levels) >= 2) {
    age1_data <- chronic_derm_with_phq[age_group == "<65"]
    age2_data <- chronic_derm_with_phq[age_group == "65+"]
    
    if(nrow(age1_data) >= 10 && nrow(age2_data) >= 10) {
      age1_clinical <- sum(age1_data$ever_clinical)
      age1_total <- nrow(age1_data)
      age2_clinical <- sum(age2_data$ever_clinical)
      age2_total <- nrow(age2_data)
      
      test_matrix <- matrix(c(age1_clinical, age1_total - age1_clinical,
                            age2_clinical, age2_total - age2_clinical), nrow = 2)
      fisher_test <- fisher.test(test_matrix)
      
      if(fisher_test$p.value < 0.05) {
        age1_rate <- round(age1_clinical/age1_total*100, 1)
        age2_rate <- round(age2_clinical/age2_total*100, 1)
        
        # Calculate OR and 95% CI
        odds_ratio <- fisher_test$estimate
        ci_lower <- fisher_test$conf.int[1]
        ci_upper <- fisher_test$conf.int[2]
        or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
        
        clinical_pairwise_results[["Age <65 vs 65+"]] <- list(
          Comparison = "<65 vs 65+",
          Group1 = paste0("<65: ", age1_clinical, "/", age1_total, " (", age1_rate, "%)"),
          Group2 = paste0("65+: ", age2_clinical, "/", age2_total, " (", age2_rate, "%)"),
          OR_CI = or_ci,
          P_Value = format_pvalue(fisher_test$p.value),
          Variable = "Age"
        )
      }
    }
  }
  
  # Race pairwise comparisons
  race_levels <- chronic_derm_with_phq[!is.na(race_refined) & race_refined != "" & 
                                      !grepl("Unknown|Other|Declined|NA", race_refined, ignore.case = TRUE), 
                                      .(n = .N, clinical_n = sum(ever_clinical), clinical_rate = round(mean(ever_clinical)*100,1)), 
                                      by = race_refined]
  
  # Only include races with ≥5% of total cohort
  race_levels <- race_levels[n >= total_n * 0.05]
  
  if(nrow(race_levels) >= 2) {
    race_list <- race_levels$race_refined
    for(i in 1:(length(race_list)-1)) {
      for(j in (i+1):length(race_list)) {
        race1 <- race_list[i]
        race2 <- race_list[j]
        
        race1_data <- chronic_derm_with_phq[race_refined == race1]
        race2_data <- chronic_derm_with_phq[race_refined == race2]
        
        if(nrow(race1_data) >= 10 && nrow(race2_data) >= 10) {
          race1_clinical <- sum(race1_data$ever_clinical)
          race1_total <- nrow(race1_data)
          race2_clinical <- sum(race2_data$ever_clinical)
          race2_total <- nrow(race2_data)
          
          test_matrix <- matrix(c(race1_clinical, race1_total - race1_clinical,
                                race2_clinical, race2_total - race2_clinical), nrow = 2)
          fisher_test <- fisher.test(test_matrix)
          
          if(fisher_test$p.value < 0.05) {
            race1_rate <- round(race1_clinical/race1_total*100, 1)
            race2_rate <- round(race2_clinical/race2_total*100, 1)
            
            # Calculate OR and 95% CI
            odds_ratio <- fisher_test$estimate
            ci_lower <- fisher_test$conf.int[1]
            ci_upper <- fisher_test$conf.int[2]
            or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
            
            clinical_pairwise_results[[paste("Race", race1, "vs", race2)]] <- list(
              Comparison = paste(race1, "vs", race2),
              Group1 = paste0(race1, ": ", race1_clinical, "/", race1_total, " (", race1_rate, "%)"),
              Group2 = paste0(race2, ": ", race2_clinical, "/", race2_total, " (", race2_rate, "%)"),
              OR_CI = or_ci,
              P_Value = format_pvalue(fisher_test$p.value),
              Variable = "Race"
            )
          }
        }
      }
    }
  }
  
  # Insurance pairwise comparisons (if available)
  if("fin_class" %in% names(chronic_derm_with_phq)) {
    insurance_levels <- chronic_derm_with_phq[!is.na(fin_class) & fin_class != "" & 
                                            !grepl("Unknown|Other|Declined|NA", fin_class, ignore.case = TRUE), 
                                            .(n = .N, clinical_n = sum(ever_clinical), clinical_rate = round(mean(ever_clinical)*100,1)), 
                                            by = fin_class]
    
    # Only include insurance types with ≥5% of total cohort
    insurance_levels <- insurance_levels[n >= total_n * 0.05]
    
    if(nrow(insurance_levels) >= 2) {
      insurance_list <- insurance_levels$fin_class
      for(i in 1:(length(insurance_list)-1)) {
        for(j in (i+1):length(insurance_list)) {
          ins1 <- insurance_list[i]
          ins2 <- insurance_list[j]
          
          ins1_data <- chronic_derm_with_phq[fin_class == ins1]
          ins2_data <- chronic_derm_with_phq[fin_class == ins2]
          
          if(nrow(ins1_data) >= 10 && nrow(ins2_data) >= 10) {
            ins1_clinical <- sum(ins1_data$ever_clinical)
            ins1_total <- nrow(ins1_data)
            ins2_clinical <- sum(ins2_data$ever_clinical)
            ins2_total <- nrow(ins2_data)
            
            test_matrix <- matrix(c(ins1_clinical, ins1_total - ins1_clinical,
                                  ins2_clinical, ins2_total - ins2_clinical), nrow = 2)
            fisher_test <- fisher.test(test_matrix)
            
            if(fisher_test$p.value < 0.05) {
              ins1_rate <- round(ins1_clinical/ins1_total*100, 1)
              ins2_rate <- round(ins2_clinical/ins2_total*100, 1)
              
              # Calculate OR and 95% CI
              odds_ratio <- fisher_test$estimate
              ci_lower <- fisher_test$conf.int[1]
              ci_upper <- fisher_test$conf.int[2]
              or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
              
              clinical_pairwise_results[[paste("Insurance", ins1, "vs", ins2)]] <- list(
                Comparison = paste(ins1, "vs", ins2),
                Group1 = paste0(ins1, ": ", ins1_clinical, "/", ins1_total, " (", ins1_rate, "%)"),
                Group2 = paste0(ins2, ": ", ins2_clinical, "/", ins2_total, " (", ins2_rate, "%)"),
                OR_CI = or_ci,
                P_Value = format_pvalue(fisher_test$p.value),
                Variable = "Insurance"
              )
            }
          }
        }
      }
    }
  }
  
  if(length(clinical_pairwise_results) > 0) {
    clinical_pairwise_df <- data.frame(
      Variable = sapply(clinical_pairwise_results, function(x) x$Variable),
      Comparison = sapply(clinical_pairwise_results, function(x) x$Comparison),
      Group1 = sapply(clinical_pairwise_results, function(x) x$Group1),
      Group2 = sapply(clinical_pairwise_results, function(x) x$Group2),
      OR_CI = sapply(clinical_pairwise_results, function(x) x$OR_CI),
      P_Value = sapply(clinical_pairwise_results, function(x) x$P_Value),
      stringsAsFactors = FALSE
    )
    
    clinical_pairwise_table <- clinical_pairwise_df %>%
      gt() %>%
      tab_header(
        title = "Supplementary Table 4. Black Patients With Lupus Erythematosus Show Markedly Higher Depression Rates Than White Patients",
        subtitle = "Within-condition pairwise comparisons showing significant depression rate differences by demographics. Limited to demographic levels representing ≥10% of condition population. Clinical depression defined as PHQ-9 score ≥10; subclinical depression defined as PHQ-9 score 5-9."
      ) %>%
      cols_label(
        Variable = "Variable",
        Comparison = "Comparison",
        Group1 = md("Group 1<br>*n* (%)"),
        Group2 = md("Group 2<br>*n* (%)"),
        OR_CI = "OR (95% CI)",
        P_Value = "*P*"
      ) %>%
      cols_align(align = "center", columns = c(OR_CI, P_Value)) %>%
      cols_align(align = "left", columns = c(Variable, Comparison, Group1, Group2)) %>%
      tab_options(
        table.border.top.color = "#000000",
        table.border.top.style = "solid",
        table.border.top.width = px(2),
        table.border.bottom.color = "#000000",
        table.border.bottom.style = "solid",
        table.border.bottom.width = px(2),
        table.border.left.style = "none",
        table.border.right.style = "none",
        column_labels.border.top.color = "#000000",
        column_labels.border.top.width = px(1),
        column_labels.border.bottom.color = "#000000",
        column_labels.border.bottom.width = px(1),
        column_labels.background.color = "#ffffff",
        column_labels.font.size = px(11),
        column_labels.font.weight = "bold",
        table.font.size = px(10),
        table.font.names = c("Times New Roman", "Times", "serif"),
        data_row.padding = px(4),
        row.striping.include_table_body = FALSE,
        table.width = pct(100),
        table.align = "center"
      ) %>%
      tab_style(
        style = list(cell_text(size = px(12), weight = "bold", align = "center")),
        locations = cells_title("title")
      ) %>%
      tab_style(
        style = list(cell_text(size = px(10), style = "italic", align = "center")),
        locations = cells_title("subtitle")
      ) %>%
      tab_footnote(
        footnote = "Fisher exact test. Only significant comparisons shown (*P* < 0.05).",
        locations = cells_column_labels(columns = P_Value)
      )
    
    print(clinical_pairwise_table)
    
    # Save as CSV
    csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
    if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
    write.csv(clinical_pairwise_df, file.path(csv_dir, "Clinical_Pairwise_Demographic_Comparisons.csv"), row.names = FALSE)
  } else {
    cat("No significant pairwise differences found between demographic levels for clinical depression.\n")
  }
} else {
  cat("Insufficient data for pairwise demographic comparisons.\n")
}
```

#### Table 2A: Clinical Depression Rates by Condition

```{r}
# Create patient_condition_pairs from master datasets (needed for compatibility)
patient_condition_pairs_list <- list()
for(condition_name in names(chronic_derm_patient_conditions)) {
  condition_patients <- chronic_derm_patient_conditions[[condition_name]]
  if(length(condition_patients) > 0) {
    patient_condition_pairs_list[[condition_name]] <- data.table(
      mrn_deid = condition_patients,
      condition_type = condition_name
    )
  }
}
patient_condition_pairs <- rbindlist(patient_condition_pairs_list)
setDT(patient_condition_pairs)

# Simple descriptive table of clinical depression rates by condition
chronic_with_conditions <- merge(chronic_derm_phq_status, 
                                patient_condition_pairs, 
                                by = "mrn_deid", all.x = TRUE)

clinical_by_condition <- chronic_with_conditions[!is.na(condition_type), .(
  n_patients = .N,
  clinical_n = sum(ever_clinical),
  clinical_rate = round(mean(ever_clinical) * 100, 1)
), by = condition_type][n_patients >= nrow(chronic_derm_phq_status) * 0.05][order(-clinical_rate)]

if(nrow(clinical_by_condition) > 0) {
  clinical_by_condition[, display := paste0(clinical_n, " (", clinical_rate, "%)")]
  
  clinical_condition_table <- clinical_by_condition[, .(condition_type, n_patients, display)] %>%
    gt() %>%
    tab_header(
      title = "Table 2. Clinical Depression by Condition",
      subtitle = "Ranked by clinical depression rate"
    ) %>%
    cols_label(
      condition_type = "Dermatologic Condition",
      n_patients = "Total *N*",
      display = md("Clinical Depression<br>*n* (%)")
    ) %>%
    cols_align(align = "left", columns = condition_type) %>%
    cols_align(align = "center", columns = c(n_patients, display)) %>%
    tab_options(
      table.border.top.color = "#000000",
      table.border.top.style = "solid",
      table.border.top.width = px(2),
      table.border.bottom.color = "#000000",
      table.border.bottom.style = "solid",
      table.border.bottom.width = px(2),
      table.border.left.style = "none",
      table.border.right.style = "none",
      column_labels.font.size = px(11),
      column_labels.font.weight = "bold",
      table.font.size = px(10),
      table.font.names = c("Times New Roman", "Times", "serif"),
      data_row.padding = px(4),
      table.width = pct(100),
      table.align = "center"
    ) %>%
    tab_style(
      style = list(cell_text(size = px(12), weight = "bold", align = "center")),
      locations = cells_title("title")
    ) %>%
    tab_style(
      style = list(cell_text(size = px(10), style = "italic", align = "center")),
      locations = cells_title("subtitle")
    ) %>%
    tab_footnote(
      footnote = "Conditions representing <5% of cohort excluded.",
      locations = cells_column_labels(columns = condition_type)
    )
  
  print(clinical_condition_table)
  
  # Save as CSV
  csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
  if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
  write.csv(clinical_by_condition[, .(condition_type, n_patients, clinical_n, clinical_rate)], 
            file.path(csv_dir, "Table_2_Clinical_Depression_by_Condition.csv"), row.names = FALSE)
} else {
  cat("No conditions meet minimum size criteria.\n")
}
```

#### Table 3A: Pairwise Clinical Depression Comparisons Between Conditions

```{r}
# Pairwise comparisons of clinical depression rates between conditions
conditions <- unique(patient_condition_pairs$condition_type)
clinical_pairwise_results <- list()

for(i in 1:(length(conditions)-1)) {
  for(j in (i+1):length(conditions)) {
    cond1 <- conditions[i]
    cond2 <- conditions[j]
    
    cond1_patients <- patient_condition_pairs[condition_type == cond1, mrn_deid]
    cond2_patients <- patient_condition_pairs[condition_type == cond2, mrn_deid]
    
    cond1_data <- chronic_derm_phq_status[mrn_deid %in% cond1_patients]
    cond2_data <- chronic_derm_phq_status[mrn_deid %in% cond2_patients]
    
    # Only compare if both conditions have sufficient sample sizes
    if(nrow(cond1_data) >= 10 && nrow(cond2_data) >= 10) {
      cond1_clinical <- sum(cond1_data$ever_clinical)
      cond1_total <- nrow(cond1_data)
      cond2_clinical <- sum(cond2_data$ever_clinical)
      cond2_total <- nrow(cond2_data)
      
      # Create 2x2 contingency table
      test_matrix <- matrix(c(
        cond1_clinical, cond1_total - cond1_clinical,
        cond2_clinical, cond2_total - cond2_clinical
      ), nrow = 2, byrow = TRUE)
      
      fisher_test <- fisher.test(test_matrix)
      
      # Store all comparisons with effect sizes
      cond1_rate <- round(cond1_clinical/cond1_total*100, 1)
      cond2_rate <- round(cond2_clinical/cond2_total*100, 1)
      rate_diff <- abs(cond1_rate - cond2_rate)
      
      # Calculate OR and 95% CI
      odds_ratio <- fisher_test$estimate
      ci_lower <- fisher_test$conf.int[1]
      ci_upper <- fisher_test$conf.int[2]
      or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
      
      clinical_pairwise_results[[paste(cond1, "vs", cond2)]] <- list(
        Comparison = paste(cond1, "vs", cond2),
        Condition1_Rate = paste0(cond1, ": ", cond1_clinical, "/", cond1_total, " (", cond1_rate, "%)"),
        Condition2_Rate = paste0(cond2, ": ", cond2_clinical, "/", cond2_total, " (", cond2_rate, "%)"),
        Rate_Difference = paste0(rate_diff, "%"),
        OR_CI = or_ci,
        P_Value = format_pvalue(fisher_test$p.value),
        significant = fisher_test$p.value < 0.05
      )
    }
  }
}

# Show only significant results (p < 0.05)
if(length(clinical_pairwise_results) > 0) {
  # Only significant results
  significant_results <- clinical_pairwise_results[sapply(clinical_pairwise_results, function(x) x$significant)]
  
  # Sort by p-value (most significant first)
  if(length(significant_results) > 0) {
    p_values <- sapply(significant_results, function(x) {
      p_str <- x$P_Value
      if(p_str == "<0.001") return(0.0005)
      return(as.numeric(p_str))
    })
    significant_results <- significant_results[order(p_values)]
  }
  
  display_results <- significant_results
  
  if(length(display_results) > 0) {
    clinical_pairwise_df <- data.frame(
      Comparison = sapply(display_results, function(x) x$Comparison),
      Condition1_Rate = sapply(display_results, function(x) x$Condition1_Rate),
      Condition2_Rate = sapply(display_results, function(x) x$Condition2_Rate),
      Rate_Difference = sapply(display_results, function(x) x$Rate_Difference),
      OR_CI = sapply(display_results, function(x) x$OR_CI),
      P_Value = sapply(display_results, function(x) x$P_Value),
      stringsAsFactors = FALSE
    )
    
    clinical_pairwise_table <- clinical_pairwise_df %>%
      gt() %>%
      tab_header(
        title = "Supplementary Table 3. Hidradenitis Suppurativa Shows Significantly Higher Clinical Depression Rates Than Most Other Dermatologic Conditions",
        subtitle = "Pairwise comparisons between chronic dermatologic conditions showing significant differences (P < .05). Statistical tests performed using Fisher exact test. Rate difference calculated as absolute percentage point difference."
      ) %>%
      cols_label(
        Comparison = "Comparison",
        Condition1_Rate = "Condition 1",
        Condition2_Rate = "Condition 2", 
        Rate_Difference = "Rate Diff",
        OR_CI = "OR (95% CI)",
        P_Value = "P-value"
      ) %>%
      tab_options(
        table.border.top.color = "#495057",
        table.border.top.width = px(3),
        table.border.bottom.color = "#495057",
        table.border.bottom.width = px(2),
        column_labels.font.weight = "bold",
        column_labels.font.size = px(13),
        table.font.size = px(13),
        table.font.names = c("Arial", "Calibri", "Segoe UI", "sans-serif")
      ) %>%
      tab_source_note("Significant results only (p < 0.05). Fisher's exact test.")
    
    print(clinical_pairwise_table)
  } else {
    cat("No meaningful pairwise comparisons available.\n")
  }
} else {
  cat("Insufficient data for pairwise comparisons.\n")
}
```

### Subclinical Depression Analysis (PHQ 5-9)

#### Table 1B: Subclinical Depression - Pairwise Comparisons Between Demographic Levels

```{r}
# Pairwise comparisons of subclinical depression rates between levels within each demographic variable
if(nrow(chronic_derm_with_phq) > 20) {
  subclinical_pairwise_results <- list()
  total_n <- nrow(chronic_derm_with_phq)
  
  # Sex pairwise comparisons
  sex_levels <- chronic_derm_with_phq[!is.na(sex) & sex != "", 
                                     .(n = .N, subclinical_n = sum(ever_subclinical), subclinical_rate = round(mean(ever_subclinical)*100,1)), 
                                     by = sex]
  
  # Only include sex categories with ≥5% of total cohort
  sex_levels <- sex_levels[n >= total_n * 0.05]
  
  if(nrow(sex_levels) >= 2) {
    sex_list <- sex_levels$sex
    for(i in 1:(length(sex_list)-1)) {
      for(j in (i+1):length(sex_list)) {
        sex1 <- sex_list[i]
        sex2 <- sex_list[j]
        
        sex1_data <- chronic_derm_with_phq[sex == sex1]
        sex2_data <- chronic_derm_with_phq[sex == sex2]
        
        if(nrow(sex1_data) >= 10 && nrow(sex2_data) >= 10) {
          sex1_subclinical <- sum(sex1_data$ever_subclinical)
          sex1_total <- nrow(sex1_data)
          sex2_subclinical <- sum(sex2_data$ever_subclinical)
          sex2_total <- nrow(sex2_data)
          
          test_matrix <- matrix(c(sex1_subclinical, sex1_total - sex1_subclinical,
                                sex2_subclinical, sex2_total - sex2_subclinical), nrow = 2)
          fisher_test <- fisher.test(test_matrix)
          
          if(fisher_test$p.value < 0.05) {
            sex1_rate <- round(sex1_subclinical/sex1_total*100, 1)
            sex2_rate <- round(sex2_subclinical/sex2_total*100, 1)
            
            # Calculate OR and 95% CI
            odds_ratio <- fisher_test$estimate
            ci_lower <- fisher_test$conf.int[1]
            ci_upper <- fisher_test$conf.int[2]
            or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
            
            subclinical_pairwise_results[[paste("Sex", sex1, "vs", sex2)]] <- list(
              Comparison = paste(sex1, "vs", sex2),
              Group1 = paste0(sex1, ": ", sex1_subclinical, "/", sex1_total, " (", sex1_rate, "%)"),
              Group2 = paste0(sex2, ": ", sex2_subclinical, "/", sex2_total, " (", sex2_rate, "%)"),
              OR_CI = or_ci,
              P_Value = format_pvalue(fisher_test$p.value),
              Variable = "Sex"
            )
          }
        }
      }
    }
  }
  
  # Age group comparisons (above vs below 65)
  if(!"age_group" %in% names(chronic_derm_with_phq)) {
    chronic_derm_with_phq[, age_group := ifelse(age_at_encounter >= 65, "65+", "<65")]
  }
  age_levels <- chronic_derm_with_phq[!is.na(age_group), 
                                     .(n = .N, subclinical_n = sum(ever_subclinical), subclinical_rate = round(mean(ever_subclinical)*100,1)), 
                                     by = age_group]
  
  if(nrow(age_levels) >= 2) {
    age1_data <- chronic_derm_with_phq[age_group == "<65"]
    age2_data <- chronic_derm_with_phq[age_group == "65+"]
    
    if(nrow(age1_data) >= 10 && nrow(age2_data) >= 10) {
      age1_subclinical <- sum(age1_data$ever_subclinical)
      age1_total <- nrow(age1_data)
      age2_subclinical <- sum(age2_data$ever_subclinical)
      age2_total <- nrow(age2_data)
      
      test_matrix <- matrix(c(age1_subclinical, age1_total - age1_subclinical,
                            age2_subclinical, age2_total - age2_subclinical), nrow = 2)
      fisher_test <- fisher.test(test_matrix)
      
      if(fisher_test$p.value < 0.05) {
        age1_rate <- round(age1_subclinical/age1_total*100, 1)
        age2_rate <- round(age2_subclinical/age2_total*100, 1)
        
        # Calculate OR and 95% CI
        odds_ratio <- fisher_test$estimate
        ci_lower <- fisher_test$conf.int[1]
        ci_upper <- fisher_test$conf.int[2]
        or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
        
        subclinical_pairwise_results[["Age <65 vs 65+"]] <- list(
          Comparison = "<65 vs 65+",
          Group1 = paste0("<65: ", age1_subclinical, "/", age1_total, " (", age1_rate, "%)"),
          Group2 = paste0("65+: ", age2_subclinical, "/", age2_total, " (", age2_rate, "%)"),
          OR_CI = or_ci,
          P_Value = format_pvalue(fisher_test$p.value),
          Variable = "Age"
        )
      }
    }
  }
  
  # Race pairwise comparisons
  race_levels <- chronic_derm_with_phq[!is.na(race_refined) & race_refined != "" & 
                                      !grepl("Unknown|Other|Declined|NA", race_refined, ignore.case = TRUE), 
                                      .(n = .N, subclinical_n = sum(ever_subclinical), subclinical_rate = round(mean(ever_subclinical)*100,1)), 
                                      by = race_refined]
  
  # Only include races with ≥5% of total cohort
  race_levels <- race_levels[n >= total_n * 0.05]
  
  if(nrow(race_levels) >= 2) {
    race_list <- race_levels$race_refined
    for(i in 1:(length(race_list)-1)) {
      for(j in (i+1):length(race_list)) {
        race1 <- race_list[i]
        race2 <- race_list[j]
        
        race1_data <- chronic_derm_with_phq[race_refined == race1]
        race2_data <- chronic_derm_with_phq[race_refined == race2]
        
        if(nrow(race1_data) >= 10 && nrow(race2_data) >= 10) {
          race1_subclinical <- sum(race1_data$ever_subclinical)
          race1_total <- nrow(race1_data)
          race2_subclinical <- sum(race2_data$ever_subclinical)
          race2_total <- nrow(race2_data)
          
          test_matrix <- matrix(c(race1_subclinical, race1_total - race1_subclinical,
                                race2_subclinical, race2_total - race2_subclinical), nrow = 2)
          fisher_test <- fisher.test(test_matrix)
          
          if(fisher_test$p.value < 0.05) {
            race1_rate <- round(race1_subclinical/race1_total*100, 1)
            race2_rate <- round(race2_subclinical/race2_total*100, 1)
            
            # Calculate OR and 95% CI
            odds_ratio <- fisher_test$estimate
            ci_lower <- fisher_test$conf.int[1]
            ci_upper <- fisher_test$conf.int[2]
            or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
            
            subclinical_pairwise_results[[paste("Race", race1, "vs", race2)]] <- list(
              Comparison = paste(race1, "vs", race2),
              Group1 = paste0(race1, ": ", race1_subclinical, "/", race1_total, " (", race1_rate, "%)"),
              Group2 = paste0(race2, ": ", race2_subclinical, "/", race2_total, " (", race2_rate, "%)"),
              OR_CI = or_ci,
              P_Value = format_pvalue(fisher_test$p.value),
              Variable = "Race"
            )
          }
        }
      }
    }
  }
  
  # Insurance pairwise comparisons (if available)
  if("fin_class" %in% names(chronic_derm_with_phq)) {
    insurance_levels <- chronic_derm_with_phq[!is.na(fin_class) & fin_class != "" & 
                                            !grepl("Unknown|Other|Declined|NA", fin_class, ignore.case = TRUE), 
                                            .(n = .N, subclinical_n = sum(ever_subclinical), subclinical_rate = round(mean(ever_subclinical)*100,1)), 
                                            by = fin_class]
    
    # Only include insurance types with ≥5% of total cohort
    insurance_levels <- insurance_levels[n >= total_n * 0.05]
    
    if(nrow(insurance_levels) >= 2) {
      insurance_list <- insurance_levels$fin_class
      for(i in 1:(length(insurance_list)-1)) {
        for(j in (i+1):length(insurance_list)) {
          ins1 <- insurance_list[i]
          ins2 <- insurance_list[j]
          
          ins1_data <- chronic_derm_with_phq[fin_class == ins1]
          ins2_data <- chronic_derm_with_phq[fin_class == ins2]
          
          if(nrow(ins1_data) >= 10 && nrow(ins2_data) >= 10) {
            ins1_subclinical <- sum(ins1_data$ever_subclinical)
            ins1_total <- nrow(ins1_data)
            ins2_subclinical <- sum(ins2_data$ever_subclinical)
            ins2_total <- nrow(ins2_data)
            
            test_matrix <- matrix(c(ins1_subclinical, ins1_total - ins1_subclinical,
                                  ins2_subclinical, ins2_total - ins2_subclinical), nrow = 2)
            fisher_test <- fisher.test(test_matrix)
            
            if(fisher_test$p.value < 0.05) {
              ins1_rate <- round(ins1_subclinical/ins1_total*100, 1)
              ins2_rate <- round(ins2_subclinical/ins2_total*100, 1)
              
              # Calculate OR and 95% CI
              odds_ratio <- fisher_test$estimate
              ci_lower <- fisher_test$conf.int[1]
              ci_upper <- fisher_test$conf.int[2]
              or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
              
              subclinical_pairwise_results[[paste("Insurance", ins1, "vs", ins2)]] <- list(
                Comparison = paste(ins1, "vs", ins2),
                Group1 = paste0(ins1, ": ", ins1_subclinical, "/", ins1_total, " (", ins1_rate, "%)"),
                Group2 = paste0(ins2, ": ", ins2_subclinical, "/", ins2_total, " (", ins2_rate, "%)"),
                OR_CI = or_ci,
                P_Value = format_pvalue(fisher_test$p.value),
                Variable = "Insurance"
              )
            }
          }
        }
      }
    }
  }
  
  if(length(subclinical_pairwise_results) > 0) {
    subclinical_pairwise_df <- data.frame(
      Variable = sapply(subclinical_pairwise_results, function(x) x$Variable),
      Comparison = sapply(subclinical_pairwise_results, function(x) x$Comparison),
      Group1 = sapply(subclinical_pairwise_results, function(x) x$Group1),
      Group2 = sapply(subclinical_pairwise_results, function(x) x$Group2),
      OR_CI = sapply(subclinical_pairwise_results, function(x) x$OR_CI),
      P_Value = sapply(subclinical_pairwise_results, function(x) x$P_Value),
      stringsAsFactors = FALSE
    )
    
    subclinical_pairwise_table <- subclinical_pairwise_df %>%
      gt() %>%
      tab_header(
        title = "Supplementary Table 4. Black Patients With Lupus Erythematosus Show Markedly Higher Depression Rates Than White Patients",
        subtitle = "Within-condition pairwise comparisons showing significant depression rate differences by demographics. Limited to demographic levels representing ≥10% of condition population. Clinical depression defined as PHQ-9 score ≥10; subclinical depression defined as PHQ-9 score 5-9."
      ) %>%
      cols_label(
        Variable = "Variable",
        Comparison = "Comparison",
        Group1 = "Group 1 n (%)",
        Group2 = "Group 2 n (%)",
        OR_CI = "OR (95% CI)",
        P_Value = "P-value"
      ) %>%
      tab_options(
        table.border.top.color = "#495057",
        table.border.top.width = px(3),
        table.border.bottom.color = "#495057",
        table.border.bottom.width = px(2),
        column_labels.font.weight = "bold",
        column_labels.font.size = px(13),
        table.font.size = px(13),
        table.font.names = c("Arial", "Calibri", "Segoe UI", "sans-serif")
      ) %>%
      tab_source_note("Significant differences only (p < 0.05). Categories <5% of cohort excluded. Fisher's exact test.")
    
    print(subclinical_pairwise_table)
    
    # Save as CSV
    csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
    if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
    write.csv(subclinical_pairwise_df, file.path(csv_dir, "Subclinical_Pairwise_Demographic_Comparisons.csv"), row.names = FALSE)
  } else {
    cat("No significant pairwise differences found between demographic levels for subclinical depression.\n")
  }
} else {
  cat("Insufficient data for pairwise demographic comparisons.\n")
}
```

#### Table 2B: Subclinical Depression Rates by Condition

```{r}
# Simple descriptive table of subclinical depression rates by condition
subclinical_by_condition <- chronic_with_conditions[!is.na(condition_type), .(
  n_patients = .N,
  subclinical_n = sum(ever_subclinical),
  subclinical_rate = round(mean(ever_subclinical) * 100, 1)
), by = condition_type][n_patients >= nrow(chronic_derm_phq_status) * 0.05][order(-subclinical_rate)]

if(nrow(subclinical_by_condition) > 0) {
  subclinical_by_condition[, display := paste0(subclinical_n, " (", subclinical_rate, "%)")]
  
  subclinical_condition_table <- subclinical_by_condition[, .(condition_type, n_patients, display)] %>%
    gt() %>%
    tab_header(
      title = "Supplementary Table 2. Subclinical Depression by Condition",
      subtitle = "Rates within chronic dermatology cohort"
    ) %>%
    cols_label(
      condition_type = "Condition",
      n_patients = "Total N",
      display = "Subclinical Depression n (%)"
    ) %>%
    tab_options(
      table.border.top.color = "#495057",
      table.border.top.width = px(3),
      table.border.bottom.color = "#495057",
      table.border.bottom.width = px(2),
      column_labels.font.weight = "bold",
      column_labels.font.size = px(13),
      table.font.size = px(13),
      table.font.names = c("Arial", "Calibri", "Segoe UI", "sans-serif")
    ) %>%
    tab_source_note("Conditions <5% of cohort excluded")
  
  print(subclinical_condition_table)
  
  # Save as CSV
  csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
  if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
  write.csv(subclinical_by_condition[, .(condition_type, n_patients, subclinical_n, subclinical_rate)], 
            file.path(csv_dir, "Supplementary_Table_2_Subclinical_Depression_by_Condition.csv"), row.names = FALSE)
} else {
  cat("No conditions meet minimum size criteria.\n")
}
```

#### Table 3B: Pairwise Subclinical Depression Comparisons Between Conditions

```{r}
# Pairwise comparisons of subclinical depression rates between conditions
subclinical_pairwise_results <- list()

for(i in 1:(length(conditions)-1)) {
  for(j in (i+1):length(conditions)) {
    cond1 <- conditions[i]
    cond2 <- conditions[j]
    
    cond1_patients <- patient_condition_pairs[condition_type == cond1, mrn_deid]
    cond2_patients <- patient_condition_pairs[condition_type == cond2, mrn_deid]
    
    cond1_data <- chronic_derm_phq_status[mrn_deid %in% cond1_patients]
    cond2_data <- chronic_derm_phq_status[mrn_deid %in% cond2_patients]
    
    # Only compare if both conditions have sufficient sample sizes
    if(nrow(cond1_data) >= 10 && nrow(cond2_data) >= 10) {
      cond1_subclinical <- sum(cond1_data$ever_subclinical)
      cond1_total <- nrow(cond1_data)
      cond2_subclinical <- sum(cond2_data$ever_subclinical)
      cond2_total <- nrow(cond2_data)
      
      # Create 2x2 contingency table
      test_matrix <- matrix(c(
        cond1_subclinical, cond1_total - cond1_subclinical,
        cond2_subclinical, cond2_total - cond2_subclinical
      ), nrow = 2, byrow = TRUE)
      
      fisher_test <- fisher.test(test_matrix)
      
      # Store all comparisons with effect sizes
      cond1_rate <- round(cond1_subclinical/cond1_total*100, 1)
      cond2_rate <- round(cond2_subclinical/cond2_total*100, 1)
      rate_diff <- abs(cond1_rate - cond2_rate)
      
      # Calculate OR and 95% CI
      odds_ratio <- fisher_test$estimate
      ci_lower <- fisher_test$conf.int[1]
      ci_upper <- fisher_test$conf.int[2]
      or_ci <- paste0(sprintf("%.2f", odds_ratio), " (", sprintf("%.2f", ci_lower), "-", sprintf("%.2f", ci_upper), ")")
      
      subclinical_pairwise_results[[paste(cond1, "vs", cond2)]] <- list(
        Comparison = paste(cond1, "vs", cond2),
        Condition1_Rate = paste0(cond1, ": ", cond1_subclinical, "/", cond1_total, " (", cond1_rate, "%)"),
        Condition2_Rate = paste0(cond2, ": ", cond2_subclinical, "/", cond2_total, " (", cond2_rate, "%)"),
        Rate_Difference = paste0(rate_diff, "%"),
        OR_CI = or_ci,
        P_Value = format_pvalue(fisher_test$p.value),
        significant = fisher_test$p.value < 0.05
      )
    }
  }
}

# Show only significant results (p < 0.05)
if(length(subclinical_pairwise_results) > 0) {
  # Only significant results
  significant_results <- subclinical_pairwise_results[sapply(subclinical_pairwise_results, function(x) x$significant)]
  
  # Sort by p-value 
  if(length(significant_results) > 0) {
    p_values <- sapply(significant_results, function(x) {
      p_str <- x$P_Value
      if(p_str == "<0.001") return(0.0005)
      return(as.numeric(p_str))
    })
    significant_results <- significant_results[order(p_values)]
  }
  
  display_results <- significant_results
  
  if(length(display_results) > 0) {
    subclinical_pairwise_df <- data.frame(
      Comparison = sapply(display_results, function(x) x$Comparison),
      Condition1_Rate = sapply(display_results, function(x) x$Condition1_Rate),
      Condition2_Rate = sapply(display_results, function(x) x$Condition2_Rate),
      Rate_Difference = sapply(display_results, function(x) x$Rate_Difference),
      OR_CI = sapply(display_results, function(x) x$OR_CI),
      P_Value = sapply(display_results, function(x) x$P_Value),
      stringsAsFactors = FALSE
    )
    
    subclinical_pairwise_table <- subclinical_pairwise_df %>%
      gt() %>%
      tab_header(
        title = "Supplementary Table 3B. Subclinical Depression Pairwise Comparisons Between Chronic Dermatologic Conditions",
        subtitle = "Pairwise comparisons between chronic dermatologic conditions for subclinical depression (PHQ-9 score 5-9). Statistical tests performed using Fisher exact test. Rate difference calculated as absolute percentage point difference."
      ) %>%
      cols_label(
        Comparison = "Comparison",
        Condition1_Rate = "Condition 1",
        Condition2_Rate = "Condition 2",
        Rate_Difference = "Rate Diff",
        OR_CI = "OR (95% CI)", 
        P_Value = "P-value"
      ) %>%
      tab_options(
        table.border.top.color = "#495057",
        table.border.top.width = px(3),
        table.border.bottom.color = "#495057",
        table.border.bottom.width = px(2),
        column_labels.font.weight = "bold",
        column_labels.font.size = px(13),
        table.font.size = px(13),
        table.font.names = c("Arial", "Calibri", "Segoe UI", "sans-serif")
      ) %>%
      tab_source_note("Significant results only (p < 0.05). Fisher's exact test.")
    
    print(subclinical_pairwise_table)
  } else {
    cat("No meaningful pairwise comparisons available.\n")
  }
} else {
  cat("Insufficient data for pairwise comparisons.\n")
}
```

## Save all tables as PNG 

```{r}
# Save all tables generated in this file as PNG files
cat("Saving all tables as PNG files...\n")

# Install webshot2 if needed
if (!requireNamespace("webshot2", quietly = TRUE)) {
  install.packages("webshot2")
}
library(webshot2)

# Create tables directory
tables_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/tables"
dir.create(tables_dir, recursive = TRUE, showWarnings = FALSE)

# Save basic demographic table if it exists
if (exists("demo_table")) {
  tryCatch({
    gtsave(data = demo_table, filename = file.path(tables_dir, "File03_Chronic_Derm_Cohort_Summary.png"))
    cat("✓ Chronic Derm Cohort Summary table saved\n")
  }, error = function(e) cat("✗ Error saving demo table:", e$message, "\n"))
}

# Save condition summary table if it exists  
if (exists("condition_table")) {
  tryCatch({
    gtsave(data = condition_table, filename = file.path(tables_dir, "File03_Condition_Summary.png"))
    cat("✓ Condition Summary table saved\n")
  }, error = function(e) cat("✗ Error saving condition table:", e$message, "\n"))
}

# Save clinical pairwise table if it exists
if (exists("clinical_pairwise_table")) {
  tryCatch({
    gtsave(data = clinical_pairwise_table, filename = file.path(tables_dir, "File03_Clinical_Pairwise_Comparisons.png"))
    cat("✓ Clinical Pairwise Comparisons table saved\n")
  }, error = function(e) cat("✗ Error saving clinical pairwise table:", e$message, "\n"))
}

# Save clinical condition table if it exists
if (exists("clinical_condition_table")) {
  tryCatch({
    gtsave(data = clinical_condition_table, filename = file.path(tables_dir, "File03_Clinical_Depression_by_Condition.png"))
    cat("✓ Clinical Depression by Condition table saved\n")
  }, error = function(e) cat("✗ Error saving clinical condition table:", e$message, "\n"))
}

# Save subclinical pairwise table if it exists
if (exists("subclinical_pairwise_table")) {
  tryCatch({
    gtsave(data = subclinical_pairwise_table, filename = file.path(tables_dir, "File03_Subclinical_Pairwise_Comparisons.png"))
    cat("✓ Subclinical Pairwise Comparisons table saved\n")
  }, error = function(e) cat("✗ Error saving subclinical pairwise table:", e$message, "\n"))
}

# Save subclinical condition table if it exists
if (exists("subclinical_condition_table")) {
  tryCatch({
    gtsave(data = subclinical_condition_table, filename = file.path(tables_dir, "File03_Subclinical_Depression_by_Condition.png"))
    cat("✓ Subclinical Depression by Condition table saved\n")
  }, error = function(e) cat("✗ Error saving subclinical condition table:", e$message, "\n"))
}

cat("File 03 table saving complete.\n")

cat("\n=== GENERATING SUPPLEMENTARY TABLES FOR ALL PAIRWISE COMPARISONS ===\n")

# Generate comprehensive supplementary tables with all comparisons (significant and non-significant)
if(exists("clinical_pairwise_results") && length(clinical_pairwise_results) > 0) {
  
  cat("Found", length(clinical_pairwise_results), "clinical pairwise results\n")
  
  # Add error handling for data.frame construction
  tryCatch({
    # Convert all clinical results to data frame with safe extraction
    all_clinical_results_df <- data.frame(
      Comparison = sapply(clinical_pairwise_results, function(x) if(is.null(x$Comparison)) "Unknown" else x$Comparison),
      Condition1_Rate = sapply(clinical_pairwise_results, function(x) if(is.null(x$Condition1_Rate)) "N/A" else x$Condition1_Rate),
      Condition2_Rate = sapply(clinical_pairwise_results, function(x) if(is.null(x$Condition2_Rate)) "N/A" else x$Condition2_Rate),
      Rate_Difference = sapply(clinical_pairwise_results, function(x) if(is.null(x$Rate_Difference)) "N/A" else x$Rate_Difference),
      OR_CI = sapply(clinical_pairwise_results, function(x) if(is.null(x$OR_CI)) "N/A" else x$OR_CI),
      P_Value = sapply(clinical_pairwise_results, function(x) if(is.null(x$P_Value)) "N/A" else x$P_Value),
      stringsAsFactors = FALSE
    )
    
    # Add significance indicator 
    all_clinical_results_df$Significant <- ifelse(
      all_clinical_results_df$P_Value == "<0.001" | 
      suppressWarnings(!is.na(as.numeric(gsub("<", "", all_clinical_results_df$P_Value))) & 
                       as.numeric(gsub("<", "", all_clinical_results_df$P_Value)) < 0.05), 
      "Yes", "No"
    )
  
  # Create Supplementary Table S4
  supp_table_s4 <- all_clinical_results_df %>%
    arrange(P_Value) %>%
    gt() %>%
    tab_header(
      title = "Supplementary Table S4. Complete Clinical Depression Comparisons Between Chronic Dermatologic Conditions",
      subtitle = "All pairwise comparisons between chronic dermatologic conditions for clinical depression (PHQ-9 score ≥10). Statistical tests performed using Fisher exact test."
    ) %>%
    cols_label(
      Comparison = "Comparison",
      Condition1_Rate = md("Condition 1<br>*n* (%)"),
      Condition2_Rate = md("Condition 2<br>*n* (%)"),
      Rate_Difference = "Rate Diff (%)",
      OR_CI = "OR (95% CI)",
      P_Value = "*P*-value",
      Significant = "Significant"
    ) %>%
    cols_align(align = "left", columns = Comparison) %>%
    cols_align(align = "center", columns = c(Condition1_Rate, Condition2_Rate, Rate_Difference, OR_CI, P_Value, Significant)) %>%
    # Highlight significant results
    tab_style(
      style = cell_fill(color = "#E8F4FD"),
      locations = cells_body(rows = Significant == "Yes")
    ) %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_body(columns = c(OR_CI, P_Value), rows = Significant == "Yes")
    ) %>%
    # Apply publication formatting
    tab_options(
      table.border.top.color = "#000000",
      table.border.top.style = "solid",
      table.border.top.width = px(2),
      table.border.bottom.color = "#000000",
      table.border.bottom.style = "solid", 
      table.border.bottom.width = px(2),
      table.border.left.style = "none",
      table.border.right.style = "none",
      column_labels.font.size = px(11),
      column_labels.font.weight = "bold",
      table.font.size = px(10),
      table.font.names = c("Times New Roman", "Times", "serif"),
      data_row.padding = px(4),
      table.width = pct(100),
      table.align = "center"
    ) %>%
    tab_style(
      style = list(cell_text(size = px(12), weight = "bold", align = "center")),
      locations = cells_title("title")
    ) %>%
    tab_style(
      style = list(cell_text(size = px(10), style = "italic", align = "center")),
      locations = cells_title("subtitle")
    ) %>%
    tab_footnote(
      footnote = "Blue highlighting indicates statistically significant comparisons (*P* < 0.05). Fisher exact test used for all comparisons. Categories representing <5% of cohort excluded from analysis.",
      locations = cells_column_labels(columns = Significant)
    )
  
  print(supp_table_s4)
  
  # Save as CSV
  csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
  if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
  write.csv(all_clinical_results_df, file.path(csv_dir, "Supplementary_Table_S4_All_Clinical_Comparisons.csv"), row.names = FALSE)
  
    # Save Supplementary Table S4
    tryCatch({
      gtsave(supp_table_s4, filename = file.path(tables_dir, "Supplementary_Table_S4_All_Clinical_Comparisons.png"))
      cat("✓ Supplementary Table S4 (All Clinical Comparisons) saved\n")
    }, error = function(e) cat("✗ Error saving Supplementary Table S4:", e$message, "\n"))
    
  }, error = function(e) {
    cat("✗ Error creating clinical supplementary table:", e$message, "\n")
    cat("Clinical pairwise results structure issues - may need to re-run earlier sections\n")
  })
  
} else {
  cat("No clinical pairwise results available for supplementary table\n")
}

# Supplementary Table S5 for subclinical comparisons if they exist
if(exists("subclinical_pairwise_results") && length(subclinical_pairwise_results) > 0) {
  
  cat("Found", length(subclinical_pairwise_results), "subclinical pairwise results\n")
  
  tryCatch({
    all_subclinical_results_df <- data.frame(
      Comparison = sapply(subclinical_pairwise_results, function(x) if(is.null(x$Comparison)) "Unknown" else x$Comparison),
      Condition1_Rate = sapply(subclinical_pairwise_results, function(x) if(is.null(x$Condition1_Rate)) "N/A" else x$Condition1_Rate),
      Condition2_Rate = sapply(subclinical_pairwise_results, function(x) if(is.null(x$Condition2_Rate)) "N/A" else x$Condition2_Rate),
      Rate_Difference = sapply(subclinical_pairwise_results, function(x) if(is.null(x$Rate_Difference)) "N/A" else x$Rate_Difference),
      OR_CI = sapply(subclinical_pairwise_results, function(x) if(is.null(x$OR_CI)) "N/A" else x$OR_CI),
      P_Value = sapply(subclinical_pairwise_results, function(x) if(is.null(x$P_Value)) "N/A" else x$P_Value),
      stringsAsFactors = FALSE
    )
    
    all_subclinical_results_df$Significant <- ifelse(
      all_subclinical_results_df$P_Value == "<0.001" | 
      suppressWarnings(!is.na(as.numeric(gsub("<", "", all_subclinical_results_df$P_Value))) & 
                       as.numeric(gsub("<", "", all_subclinical_results_df$P_Value)) < 0.05), 
      "Yes", "No"
    )
  
  supp_table_s5 <- all_subclinical_results_df %>%
    arrange(P_Value) %>%
    gt() %>%
    tab_header(
      title = "Supplementary Table S5. Complete Subclinical Depression Comparisons Between Chronic Dermatologic Conditions",
      subtitle = "All pairwise comparisons between chronic dermatologic conditions for subclinical depression (PHQ-9 score 5-9). Statistical tests performed using Fisher exact test."
    ) %>%
    cols_label(
      Comparison = "Comparison",
      Condition1_Rate = md("Condition 1<br>*n* (%)"),
      Condition2_Rate = md("Condition 2<br>*n* (%)"),
      Rate_Difference = "Rate Diff (%)",
      OR_CI = "OR (95% CI)",
      P_Value = "*P*-value",
      Significant = "Significant"
    ) %>%
    cols_align(align = "left", columns = Comparison) %>%
    cols_align(align = "center", columns = c(Condition1_Rate, Condition2_Rate, Rate_Difference, OR_CI, P_Value, Significant)) %>%
    tab_style(
      style = cell_fill(color = "#FFF2E8"),  # Different color for subclinical
      locations = cells_body(rows = Significant == "Yes")
    ) %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_body(columns = c(OR_CI, P_Value), rows = Significant == "Yes")
    ) %>%
    # Same publication formatting as S4
    tab_options(
      table.border.top.color = "#000000",
      table.border.top.style = "solid",
      table.border.top.width = px(2),
      table.border.bottom.color = "#000000",
      table.border.bottom.style = "solid",
      table.border.bottom.width = px(2),
      table.border.left.style = "none",
      table.border.right.style = "none",
      column_labels.font.size = px(11),
      column_labels.font.weight = "bold",
      table.font.size = px(10),
      table.font.names = c("Times New Roman", "Times", "serif"),
      data_row.padding = px(4),
      table.width = pct(100)
    ) %>%
    tab_style(
      style = list(cell_text(size = px(12), weight = "bold", align = "center")),
      locations = cells_title("title")
    ) %>%
    tab_style(
      style = list(cell_text(size = px(10), style = "italic", align = "center")),
      locations = cells_title("subtitle")
    ) %>%
    tab_footnote(
      footnote = "Orange highlighting indicates statistically significant comparisons (*P* < 0.05). Fisher exact test used for all comparisons.",
      locations = cells_column_labels(columns = Significant)
    )
  
  print(supp_table_s5)
  
  # Save as CSV
  csv_dir <- "C:/Users/dkucirek/Documents/Derm-SRP/As CSV"
  if (!dir.exists(csv_dir)) dir.create(csv_dir, recursive = TRUE)
  write.csv(all_subclinical_results_df, file.path(csv_dir, "Supplementary_Table_S5_All_Subclinical_Comparisons.csv"), row.names = FALSE)
  
    # Save Supplementary Table S5
    tryCatch({
      gtsave(supp_table_s5, filename = file.path(tables_dir, "Supplementary_Table_S5_All_Subclinical_Comparisons.png"))
      cat("✓ Supplementary Table S5 (All Subclinical Comparisons) saved\n")
    }, error = function(e) cat("✗ Error saving Supplementary Table S5:", e$message, "\n"))
    
  }, error = function(e) {
    cat("✗ Error creating subclinical supplementary table:", e$message, "\n")
    cat("Subclinical pairwise results structure issues - may need to re-run earlier sections\n")
  })
  
} else {
  cat("No subclinical pairwise results available for supplementary table\n")
}

cat("✓ Supplementary material generation complete\n")

print(as.data.frame(depression_summary))
print(as.data.frame(demo_summary))
print(as.data.frame(condition_summary))

length(clinical_pairwise_results)
sapply(clinical_pairwise_results, function(x) x$P_Value)
sapply(clinical_pairwise_results, function(x) x$significant)

```


