---
title: "05: Plots"
output: html_document
---

This script is the fifth and final step in the analysis pipeline. It performs the following actions:

1.  **Loads Cohort Data**: It loads the `result_wide.rds`, `chronic_derm_cohort.rds`, and `derm_clinic_cohort.rds` files created in the previous steps.
2.  **Generates Plots**: It generates a series of plots to visualize the results of the analyses, including:
    *   A comparison of PHQ positivity rates between the "Derm Clinic" and "Non-Derm" cohorts.
    *   A comparison of PHQ positivity rates for various dermatological conditions.
    *   A plot of dermatological conditions with significantly higher PHQ positivity rates.
    *   A plot of encounter counts for specific dermatological ICD-10 codes.
    *   A Sankey diagram showing the change in patient PHQ-2 status after a chronic derm diagnosis.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Libraries and Data

```{r}
library(data.table)
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(networkD3)
library(htmlwidgets)

# --- Configuration: Set your data path here ---
data_path <- "Z:/Kucirek/"

# --- Load Pre-processed Data ---
result_wide_all <- readRDS(file.path(data_path, "result_wide.rds"))
chronic_derm_cohort <- readRDS(file.path(data_path, "chronic_derm_cohort.rds"))
derm_clinic_cohort <- readRDS(file.path(data_path, "derm_clinic_cohort.rds"))

setDT(result_wide_all)
setDT(chronic_derm_cohort)
setDT(derm_clinic_cohort)
```

### Derm vs. Non-Derm Plots

```{r}
# --- Helper Functions ---
calculate_phq_positivity_dt <- function(dt) {
  if (nrow(dt) == 0) return(list(n_patients = 0, phq2_pos_count = 0, phq9_pos_count = 0))
  phq_summary <- dt[, .(
    phq2_pos = any((`phq_value_CMS PHQ-2 POS/NEG` == "Positive") | (phq2_manual_posneg == "Positive"), na.rm = TRUE),
    phq9_pos = any((`phq_value_CMS PHQ-9 POS/NEG` == "Positive") |
                   (!is.na(`phq_value_num_PHQ-9 Total Score`) & `phq_value_num_PHQ-9 Total Score` >= 10) |
                   (!is.na(phq9_manual_sum) & phq9_manual_sum >= 10), na.rm = TRUE)
  ), by = mrn_deid]
  return(list(
    n_patients = uniqueN(phq_summary$mrn_deid),
    phq2_pos_count = sum(phq_summary$phq2_pos, na.rm = TRUE),
    phq9_pos_count = sum(phq_summary$phq9_pos, na.rm = TRUE)
  ))
}

get_p_value <- function(group1_stats, group2_stats, phq_type) {
  pos1 <- if (phq_type == "PHQ-2") group1_stats$phq2_pos_count else group1_stats$phq9_pos_count
  neg1 <- group1_stats$n_patients - pos1
  pos2 <- if (phq_type == "PHQ-2") group2_stats$phq2_pos_count else group2_stats$phq9_pos_count
  neg2 <- group2_stats$n_patients - pos2
  mat <- matrix(c(pos1, neg1, pos2, neg2), nrow = 2, byrow = TRUE)
  if(any(is.na(mat)) || any(mat < 0)) return(NA)
  test_result <- tryCatch(chisq.test(mat, correct = TRUE), error = function(e) list(p.value = NA))
  return(test_result$p.value)
}

significance_stars <- function(p) {
  case_when(is.na(p) ~ "", p < 0.001 ~ "***", p < 0.01 ~ "**", p < 0.05 ~ "*", TRUE ~ "")
}

# --- Define Cohorts and Calculate Rates ---
non_derm_cohort <- result_wide_all[!mrn_deid %in% unique(derm_clinic_cohort$mrn_deid)]

stats_non_derm <- calculate_phq_positivity_dt(non_derm_cohort)
stats_derm_clinic <- calculate_phq_positivity_dt(derm_clinic_cohort)
stats_chronic_derm <- calculate_phq_positivity_dt(chronic_derm_cohort)

plot_df <- data.frame(
  Cohort = c("Chronic Derm", "Derm Clinic Cohort", "Non-Derm"),
  N = c(stats_chronic_derm$n_patients, stats_derm_clinic$n_patients, stats_non_derm$n_patients),
  PHQ2_Rate = c(stats_chronic_derm$phq2_pos_count / stats_chronic_derm$n_patients,
                stats_derm_clinic$phq2_pos_count / stats_derm_clinic$n_patients,
                stats_non_derm$phq2_pos_count / stats_non_derm$n_patients),
  PHQ9_Rate = c(stats_chronic_derm$phq9_pos_count / stats_chronic_derm$n_patients,
                stats_derm_clinic$phq9_pos_count / stats_derm_clinic$n_patients,
                stats_non_derm$phq9_pos_count / stats_non_derm$n_patients)
)

plot_df$PHQ2_Rate_Formatted <- paste0(round(plot_df$PHQ2_Rate * 100, 1), "%")
plot_df$PHQ9_Rate_Formatted <- paste0(round(plot_df$PHQ9_Rate * 100, 1), "%")

plot_df$p_val_phq2 <- sapply(list(stats_chronic_derm, stats_derm_clinic, stats_non_derm), get_p_value, stats_non_derm, "PHQ-2")
plot_df$p_val_phq9 <- sapply(list(stats_chronic_derm, stats_derm_clinic, stats_non_derm), get_p_value, stats_non_derm, "PHQ-9")

plot_df$sig_phq2 <- significance_stars(plot_df$p_val_phq2)
plot_df$sig_phq9 <- significance_stars(plot_df$p_val_phq9)

# --- Generate Plots ---
create_comparison_plot <- function(data, rate_col, sig_col, title) {
  rate_col_sym <- sym(rate_col)
  sig_col_sym <- sym(sig_col)
  formatted_rate_col_sym <- sym(paste0(rate_col, "_Formatted"))

  data$Cohort <- factor(data$Cohort, levels = c("Non-Derm", "Derm Clinic Cohort", "Chronic Derm"))

  ggplot(data, aes(x = Cohort, y = !!rate_col_sym, fill = Cohort)) +
    geom_bar(stat = "identity", color = "black", width = 0.7) +
    geom_text(aes(label = !!formatted_rate_col_sym),
              vjust = -0.5,
              size = 5, fontface = "bold", color = "black") +
    geom_text(aes(label = !!sig_col_sym, y = !!rate_col_sym + 0.03),
              size = 8, color = "black") +
    labs(title = title, subtitle = "Compared to Non-Dermatology Patients", x = NULL, y = "Positive Screening Rate") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                       expand = expansion(mult = c(0, 0.25))) +
    scale_fill_manual(values = c("Chronic Derm" = "#D55E00", "Derm Clinic Cohort" = "#009E73", "Non-Derm" = "#56B4E9")) +
    theme_minimal(base_size = 16) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 20),
      plot.subtitle = element_text(hjust = 0.5, size = 14, color = "gray30"),
      legend.position = "none",
      axis.text.x = element_text(face = "bold", size = 14),
      axis.title.y = element_text(face = "bold", margin = margin(r = 10)),
      plot.margin = margin(1, 1, 1, 1, "cm")
    )
}

plot_phq2 <- create_comparison_plot(plot_df, "PHQ2_Rate", "sig_phq2", "Comparison of PHQ-2 Positivity Rates Across Patient Cohorts")
print(plot_phq2)

plot_phq9 <- create_comparison_plot(plot_df, "PHQ9_Rate", "sig_phq9", "Comparison of PHQ-9 Positivity Rates Across Patient Cohorts")
print(plot_phq9)
```

### Derm Conditions Screening Plots

```{r}
# --- Define Chronic Dermatological Conditions ---
chronic_condition_terms <- list(
  "Scarring Alopecia" = c("lichen planopilaris", "lichen plano-pilaris", "central centrifugal cicatricial alopecia", "cicatricial alopecia", "Alopecia, scarring", "Scarring alopecia"),
  "Acne" = c("acne vulgaris", "other acne", "acne, unspecified acne type", "nodulocystic acne", "cystic acne", "acne keloidalis nuchae", "cystic acne vulgaris", "inflammatory acne"),
  "Hidradenitis Suppurativa" = "hidradenitis suppurativa",
  "Rosacea" = "rosacea",
  "Vitiligo" = "vitiligo",
  "Atopic Dermatitis" = c("intrinsic atopic dermatitis", "atopic dermatitis, unspecified type", "other atopic dermatitis", "atopic dermatitis"),
  "Psoriasis" = "psoriasis",
  "Lupus Erythematosus" = "lupus erythematosus",
  "Alopecia Areata" = c("Alopecia areata", "Alopecia areata totalis")
)

# --- Create Cohorts, Calculate Rates and P-values ---
non_chronic_cohort <- derm_clinic_cohort[!mrn_deid %in% unique(chronic_derm_cohort$mrn_deid)]

stats_non_chronic <- calculate_phq_positivity_dt(non_chronic_cohort)

plot_data_list <- lapply(names(chronic_condition_terms), function(name) {
  terms <- chronic_condition_terms[[name]]
  if (length(terms) > 1) {
    mrns <- chronic_derm_cohort[tolower(icd_diagnosis) %in% tolower(terms), unique(mrn_deid)]
  } else {
    mrns <- chronic_derm_cohort[str_detect(tolower(icd_diagnosis), tolower(terms)), unique(mrn_deid)]
  }
  cohort <- chronic_derm_cohort[mrn_deid %in% mrns]
  stats <- calculate_phq_positivity_dt(cohort)
  
  if (stats$n_patients == 0) return(NULL)
  
  data.frame(
    Cohort = name,
    N = stats$n_patients,
    PHQ2_Rate = stats$phq2_pos_count / stats$n_patients,
    PHQ9_Rate = stats$phq9_pos_count / stats$n_patients,
    p_val_phq2_vs_nc = get_p_value(stats, stats_non_chronic, "PHQ-2"),
    p_val_phq9_vs_nc = get_p_value(stats, stats_non_chronic, "PHQ-9")
  )
})

individual_rates_df <- bind_rows(plot_data_list)

# --- Generate Plots ---
create_plot <- function(data, rate_col, p_val_col, title, ref_line_rate) {
  rate_col_sym <- sym(rate_col)
  p_val_col_sym <- sym(p_val_col)
  
  data <- data %>% mutate(sig = significance_stars(!!p_val_col_sym))
  
  ggplot(data, aes(x = reorder(Cohort, !!rate_col_sym), y = !!rate_col_sym, fill = !!rate_col_sym)) +
    geom_bar(stat = "identity", color = "black", width = 0.7) +
    geom_text(aes(label = paste0(round(!!rate_col_sym * 100, 1), "%")), hjust = 1.2, size = 3.5, color = "white") +
    geom_text(aes(label = sig), hjust = -0.3, size = 5, color = "black") +
    geom_hline(aes(yintercept = ref_line_rate, linetype = "Non-Chronic Derm Rate"), color = "firebrick", size = 0.8) +
    scale_fill_gradient(low = "#56B4E9", high = "#0072B2") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.15))) +
    scale_linetype_manual(name = "", values = c("Non-Chronic Derm Rate" = "dashed")) +
    coord_flip() +
    labs(
      title = title,
      subtitle = "Compared to Non-Chronic Dermatology Patient Rate",
      x = NULL, 
      y = "Positive Screening Rate"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 18),
      plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
      axis.text.x = element_text(size = 10),
      axis.text.y = element_text(size = 10),
      axis.title.x = element_text(size = 12, margin = margin(t = 10)),
      legend.position = "bottom",
      panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_line(color = "gray90", linetype = "dotted"),
      plot.margin = margin(1, 1, 1, 1, "cm")
    ) +
    guides(fill = "none")
}

phq2_plot <- create_plot(individual_rates_df, "PHQ2_Rate", "p_val_phq2_vs_nc", "PHQ-2 Positivity by Chronic Condition", stats_non_chronic$phq2_pos_count / stats_non_chronic$n_patients)
print(phq2_plot)

phq9_plot <- create_plot(individual_rates_df, "PHQ9_Rate", "p_val_phq9_vs_nc", "PHQ-9 Positivity by Chronic Condition", stats_non_chronic$phq9_pos_count / stats_non_chronic$n_patients)
print(phq9_plot)
```

### Significant Derm Conditions Plots
```{r}
# --- Filter for Significance ---
significant_phq2 <- individual_rates_df %>%
  filter(p_val_phq2_vs_nc < 0.05 & PHQ2_Rate > (stats_non_chronic$phq2_pos_count / stats_non_chronic$n_patients)) %>%
  mutate(sig = significance_stars(p_val_phq2_vs_nc))

significant_phq9 <- individual_rates_df %>%
  filter(p_val_phq9_vs_nc < 0.05 & PHQ9_Rate > (stats_non_chronic$phq9_pos_count / stats_non_chronic$n_patients)) %>%
  mutate(sig = significance_stars(p_val_phq9_vs_nc))

# --- Generate Plots for Significant Conditions ---
create_significant_plot <- function(data, rate_col, sig_col, title, ref_line_rate) {
  rate_col_sym <- sym(rate_col)
  sig_col_sym <- sym(sig_col)
  
  if (nrow(data) == 0) {
    return(ggplot() + labs(title = title, subtitle = "No conditions with significantly higher rates found.") + theme_minimal())
  }
  
  ggplot(data, aes(x = reorder(Cohort, !!rate_col_sym), y = !!rate_col_sym, fill = Cohort)) +
    geom_bar(stat = "identity", color = "black", width = 0.7) +
    geom_text(aes(label = paste0(round(!!rate_col_sym * 100, 1), "%")), hjust = 1.2, color = "white", size = 3.5) +
    geom_text(aes(label = !!sig_col_sym), hjust = -0.3, size = 5, color = "black") +
    geom_hline(aes(yintercept = ref_line_rate, linetype = "Non-Derm Rate"), color = "firebrick", size = 0.8) +
    scale_fill_brewer(palette = "viridis") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.15))) +
    scale_linetype_manual(name = "", values = c("Non-Derm Rate" = "dashed")) +
    coord_flip() +
    labs(
      title = title,
      subtitle = "Positivity rates significantly higher than the non-dermatology patient rate",
      x = NULL, 
      y = "Positive Screening Rate"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 18),
      plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray30"),
      axis.text = element_text(size = 10),
      axis.title.x = element_text(size = 12, margin = margin(t = 10)),
      legend.position = "none",
      panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_line(color = "gray90", linetype = "dotted"),
      plot.margin = margin(t = 1.5, r = 1, b = 1, l = 1, unit = "cm")
    )
}

plot_sig_phq2 <- create_significant_plot(significant_phq2, "PHQ2_Rate", "sig", "Dermatologic Conditions with Significantly Higher PHQ-2 Positivity", stats_non_derm$phq2_pos_count / stats_non_derm$n_patients)
print(plot_sig_phq2)

plot_sig_phq9 <- create_significant_plot(significant_phq9, "PHQ9_Rate", "sig", "Dermatologic Conditions with Significantly Higher PHQ-9 Positivity", stats_non_derm$phq9_pos_count / stats_non_derm$n_patients)
print(plot_sig_phq9)
```


### ICD Counts Plot

I would also like number of patients 

```{r}
# --- Load Data ---
encounters_data <- fread(file.path(data_path, "specific_icd_encounters.csv"))

# --- Prepare Data for Plotting ---
plot_data <- encounters_data[, .N, by = icd_category]

# --- Create the Bar Chart ---
if (nrow(plot_data) > 0) {
  icd_counts_plot <- ggplot(plot_data, aes(x = reorder(icd_category, N), y = N)) +
    geom_bar(stat = "identity", fill = "#0072B2", width = 0.7) +
    coord_flip() +
    geom_text(aes(label = N), hjust = -0.2, size = 3.5, color = "black") +
    labs(
      title = "Encounter Counts for Specific Dermatological ICD-10 Codes",
      subtitle = "Total number of encounters recorded for each condition category",
      x = "ICD-10 Code Category",
      y = "Number of Encounters"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, color = "gray40"),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      panel.grid.major.y = element_blank(),
      panel.grid.minor.x = element_blank()
    )

  print(icd_counts_plot)
}
```

### Sankey Plot

```{r}
# --- Load Data ---
patient_summary <- fread(file.path(data_path, "longitudinal_patient_phq_change.csv"))

# --- Prepare Data for the Sankey Diagram ---
links <- patient_summary %>%
  group_by(ever_positive_pre, ever_positive_post) %>%
  summarise(value = n(), .groups = 'drop') %>%
  as.data.table()

nodes <- data.frame(name = c(
  "Pre-Chronic Negative", 
  "Pre-Chronic Positive", 
  "Post-Chronic Negative", 
  "Post-Chronic Positive"
))

links$source <- ifelse(links$ever_positive_pre == FALSE, 0, 1)
links$target <- ifelse(links$ever_positive_post == FALSE, 2, 3)

# --- Create the Sankey Diagram ---
my_color <- 'd3.scaleOrdinal().domain(["Pre-Chronic Negative", "Pre-Chronic Positive", "Post-Chronic Negative", "Post-Chronic Positive"]).range(["#0072B2", "#D55E00", "#0072B2", "#D55E00"])'

sankey_plot <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "source",
  Target = "target",
  Value = "value",
  NodeID = "name",
  units = "Patients",
  fontSize = 14,
  nodeWidth = 30,
  colourScale = my_color
)

sankey_plot <- htmlwidgets::prependContent(
  sankey_plot, 
  htmltools::tags$h2(
    style = "font-family: Arial, sans-serif; text-align: center;", 
    "Change in Patient PHQ-2 Status After Chronic Derm Diagnosis"
  )
)

print(sankey_plot)
```
