```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readxl)
library(data.table)

demo_cols <- c("MRN_DEID", "race", "ethnic", "sex")
demo_data <- fread("Z:/Kucirek/dr_592588_demo.csv", select = demo_cols)
setnames(demo_data, tolower(names(demo_data)))

# Depression
depression_cols <- c("MRN_DEID", "PHQ_DTTM", "PHQ_FIELD", "PHQ_VALUE")
depression_data <- fread("Z:/Kucirek/DR_592588_DEPRESSION.txt", select = depression_cols)
setnames(depression_data, tolower(names(depression_data)))

encounter_cols <- c("MRN_DEID", "age_at_encounter", "FIN_CLASS", "APPT_DEPT", "ICD10_DX", "ICD_DIAGNOSIS", "ENC_DATE")

# Load and filter for age >= 18 in one step
encounters_data <- fread(
  "Z:/Kucirek/dr_592588_encounter.txt",
  select = encounter_cols
)[age_at_encounter >= 18]

setnames(encounters_data, tolower(names(encounters_data)))

glimpse(depression_data)
```

making all columns with mrn 'trimmed'
Getting counts of unique MRNS in each of the three datasets I'm using, the Demographics, Depression screens and Encounters 
```{r}
library(data.table)
library(dplyr)

# Convert to data.table and clean MRNs
datasets <- list(demo_data, depression_data, encounters_data)
lapply(datasets, setDT)
lapply(datasets, function(dt) dt[, mrn_deid := as.character(trimws(mrn_deid))])

# Keep unique MRNs in demo_data
demo_data <- unique(demo_data, by = "mrn_deid")
cat("Unique MRNs in demo data:", uniqueN(demo_data$mrn_deid), "\n")

# Function to count non-missing PHQ responses
count_phq_responses <- function(data, phq_fields) {
  data %>%
    filter(phq_field %in% phq_fields, !is.na(phq_value), phq_value != "") %>%
    nrow()
}

# Output PHQ response counts
cat("PHQ-2 total or POS/NEG:", count_phq_responses(depression_data, c("PHQ-2 Total Score", "CMS PHQ-2 POS/NEG")), "\n")
cat("PHQ-2 POS/NEG responses:", count_phq_responses(depression_data, "CMS PHQ-2 POS/NEG"), "\n")
cat("PHQ-9 total or POS/NEG:", count_phq_responses(depression_data, c("PHQ-9 Total Score", "CMS PHQ-9 POS/NEG")), "\n")
cat("PHQ-9 Total Score responses:", count_phq_responses(depression_data, "PHQ-9 Total Score"), "\n")

# Add PHQ-9 POS/NEG only count
cat("PHQ-9 POS/NEG:", count_phq_responses(depression_data, "CMS PHQ-9 POS/NEG"), "\n")

# Merge demo and depression data on MRN
dd_merged <- merge(demo_data, depression_data, by = "mrn_deid", all = FALSE)
setDT(dd_merged)

# Report unique MRNs
cat("Unique MRNs in dd_merged:", uniqueN(dd_merged$mrn_deid), "\n")
cat("Unique MRNs in encounters_data:", uniqueN(encounters_data$mrn_deid), "\n")

```

checking if the phq9 pos/neg and total sums overlap or are all one vs the other -- so 56,859 screens have both the pos/neg and total recorded, 3178 have only pos/neg, 3382 have only total score listed, 2,229 have neither 
```{r}
library(data.table)

# Assuming depression_data is a data.table with columns: mrn_deid, phq_dttm, phq_field, phq_value

# Filter for PHQ-9 related fields
phq9_data <- depression_data[phq_field %in% c("PHQ-9 Total Score", "CMS PHQ-9 POS/NEG")]

# Summarize per MRN and phq_dttm whether Total Score and/or POS/NEG present
phq9_summary <- phq9_data[, .(
  has_total_score = any(phq_field == "PHQ-9 Total Score" & !is.na(phq_value) & phq_value != ""),
  has_posneg = any(phq_field == "CMS PHQ-9 POS/NEG" & !is.na(phq_value) & phq_value != "")
), by = .(mrn_deid, phq_dttm)]

# Count the overlap categories
overlap_counts <- phq9_summary[, .N, by = .(
  has_total_score,
  has_posneg
)]

print(overlap_counts)

sum_counts <- sum(c(56859, 2229, 3178))
print(sum_counts)
```

checking with earlier---
Total screens with Total Score = 56,859 (both) + 3,382 (only total) = 60,241

Total screens with POS/NEG = 56,859 (both) + 3,178 (only posneg) = 60,037

so this checks out 

this is good, it shows that there aren't any phq9 screens that are fully completed but not listed as complete, either pos or neg 

```{r}
library(dplyr)

# Define the PHQ-9 item fields *before* you use them
phq9_items <- c(
  "feeling down, depressed, or hopeless score",
  "little interest or pleasure in doing things score",
  "thoughts that you would be better off dead or of hurting yourself score",
  "feeling tired or having little energy score",
  "trouble falling or staying asleep, or sleep too much score",
  "poor appetite or overeating score",
  "trouble concentrating on things, such as reading the newspaper or watching television score",
  "feeling bad about yourself or that you are a failure or have let yourself or your family down score",
  "moving or speaking so slowly that other people have noticed. Or the opposite score"
)

# Summarize by patient and date (screen)
phq9_summary <- phq9_data %>%
  group_by(mrn_deid, phq_dttm) %>%
  summarize(
    has_total_score = any(phq_field == "PHQ-9 Total Score" & !is.na(phq_value)),
    has_posneg = any(phq_field == "CMS PHQ-9 POS/NEG" & !is.na(phq_value)),
    n_items_present = sum(phq_field %in% phq9_items & !is.na(phq_value)),
    .groups = "drop"
  )

# Filter screens that have neither total score nor POS/NEG
no_scores <- phq9_summary %>%
  filter(!has_total_score, !has_posneg)

# Count how many of those have all 9 PHQ-9 items present
complete_no_scores <- no_scores %>%
  filter(n_items_present == 9) %>%
  nrow()

cat("Screens with neither score but all 9 PHQ-9 items present:", complete_no_scores, "\n")

```

converting dates to Date type, defining phq fields, making window around screening times and around phq2 and 9s 
```{r}
# Convert screening dates to Date type and rename
dd_merged[, phq_date := as.Date(phq_dttm)]
encounters_data[, enc_date := as.Date(enc_date)]

# Convert PHQ values to numeric where applicable
dd_merged[, phq_value_num := fifelse(
  tolower(phq_value) %in% c("positive", "negative", ""),
  NA_real_,
  as.numeric(phq_value)
)]

# Define PHQ fields of interest (13 fields)
keep_fields <- c(
  "feeling down, depressed, or hopeless score",
  "little interest or pleasure in doing things score",
  "feeling tired or having little energy score",
  "trouble falling or staying asleep, or sleep too much score",
  "thoughts that you would be better off dead or of hurting yourself score",
  "trouble concentrating on things, such as reading the newspaper or watching television score",
  "feeling bad about yourself or that you are a failure or have let yourself or your family down score",
  "CMS PHQ-9 POS/NEG",
  "moving or speaking so slowly that other people have noticed. Or the opposite score",
  "poor appetite or overeating score",
  "PHQ-9 Total Score",
  "PHQ-2 score",
  "CMS PHQ-2 POS/NEG"
)

# Create ±1 month window around PHQ screening dates
dd_merged[, `:=`(window_start = phq_date %m-% months(1), window_end = phq_date %m+% months(1))]
encounters_data[, `:=`(enc_start = enc_date, enc_end = enc_date)]

# Set keys for data.table overlaps
setkey(dd_merged, mrn_deid, window_start, window_end)
setkey(encounters_data, mrn_deid, enc_start, enc_end)

# Join encounters with PHQ screenings within ±1 month
result_all_matches <- foverlaps(encounters_data, dd_merged,
  by.x = c("mrn_deid", "enc_start", "enc_end"),
  by.y = c("mrn_deid", "window_start", "window_end"),
  type = "any", nomatch = 0L
)

# Filter for only PHQ fields of interest
result_all_matches <- result_all_matches[phq_field %in% keep_fields]

# Compute absolute date difference between encounter and screening
result_all_matches[, date_diff := abs(as.numeric(enc_date - phq_date))]

# Keep the closest PHQ screening for each (mrn, encounter, phq_field)
result_closest_all <- result_all_matches[
  order(mrn_deid, enc_date, phq_field, date_diff)
][
  , .SD[1], by = .(mrn_deid, enc_date, phq_field)
]

cat("Unique MRNs in filtered result:", uniqueN(result_closest_all$mrn_deid), "\n")

# Pivot to wide format: one row per (mrn, encounter)
result_wide <- result_closest_all %>%
  as_tibble() %>%
  pivot_wider(
    id_cols = c(mrn_deid, enc_date),
    names_from = phq_field,
    values_from = c(phq_value, phq_value_num, phq_date),
    names_glue = "{.value}_{phq_field}"
  )

```
Now, making results wide, and manually calculating phq9 scores when all fields are filled out 
```{r}
result_wide <- result_closest_all %>%
  as_tibble() %>%
  pivot_wider(
    id_cols = c(mrn_deid, enc_date, age_at_encounter, fin_class, appt_dept, icd10_dx, icd_diagnosis),
    names_from = phq_field,
    values_from = c(phq_value, phq_value_num, phq_date),
    names_glue = "{.value}_{phq_field}"
  )
phq9_items <- c(
  "phq_value_num_feeling tired or having little energy score",
  "phq_value_num_poor appetite or overeating score",
  "phq_value_num_little interest or pleasure in doing things score",
  "phq_value_num_feeling down, depressed, or hopeless score",
  "phq_value_num_moving or speaking so slowly that other people have noticed. Or the opposite score",
  "phq_value_num_feeling bad about yourself or that you are a failure or have let yourself or your family down score",
  "phq_value_num_thoughts that you would be better off dead or of hurting yourself score",
  "phq_value_num_trouble falling or staying asleep, or sleep too much score",
  "phq_value_num_trouble concentrating on things, such as reading the newspaper or watching television score"
)

#only computing when all 9 are present 
result_wide <- result_wide %>%
  mutate(
    n_items_present = rowSums(!is.na(across(all_of(phq9_items)))),
    phq9_manual_sum = case_when(
      n_items_present == 9 ~ rowSums(across(all_of(phq9_items)), na.rm = FALSE),
      TRUE ~ NA_real_
    )
  )

# Optional: Use the actual PHQ screening date from one of the fields (if you still want phq_date)
result_wide <- result_wide %>%
  mutate(phq_date = coalesce(
    `phq_date_PHQ-9 Total Score`,
    `phq_date_CMS PHQ-9 POS/NEG`,
    `phq_date_CMS PHQ-2 POS/NEG`
  ))

cols_order <- c(
  "mrn_deid", "enc_date", "phq_date",
  "phq_value_CMS PHQ-2 POS/NEG", "phq_value_num_PHQ-2 score",
  "phq_value_CMS PHQ-9 POS/NEG", "phq_value_num_PHQ-9 Total Score",
  "phq9_manual_sum"
)

result_wide_subset <- result_wide %>%
  select(any_of(cols_order))

n_unique_encounters <- result_wide_subset %>%
  distinct(mrn_deid, enc_date, phq_date) %>%
  nrow()

n_unique_mrns <- result_wide_subset %>%
  distinct(mrn_deid) %>%
  nrow()

cat("Unique encounter combos (MRN, enc_date, phq_date):", n_unique_encounters, "\n")
cat("Unique MRNs in final result:", n_unique_mrns, "\n")

```

```{r}
library(dplyr)

result_wide_subset %>%
  mutate(
    phq9_source = case_when(
      !is.na(`phq_value_num_PHQ-9 Total Score`) ~ "PHQ-9 Total present",
      is.na(`phq_value_num_PHQ-9 Total Score`) & !is.na(phq9_manual_sum) ~ "Manual sum only",
      TRUE ~ "No PHQ-9"
    )
  ) %>%
  count(phq9_source)
```

talk with Dr Laiteerapong said some were phq8 and not 9 so calculating how many had 8 filled out. also looking at full count distribution
```{r}
result_wide %>%
  filter(n_items_present == 8) %>%
  nrow()

result_wide %>%
  count(n_items_present, sort = TRUE)

phq9_item_presence <- result_wide %>%
  summarise(across(all_of(phq9_items), ~ sum(!is.na(.)), .names = "present_{.col}")) %>%
  pivot_longer(everything(), names_to = "phq_item", values_to = "present_count") %>%
  arrange(desc(present_count))

phq9_item_presence
#so this is showing that most of the responses are actually the first two, which double as the phq

```
```{r}
library(dplyr)

# 1. PHQ-2 numeric items columns
phq2_items <- c(
  "phq_value_num_little interest or pleasure in doing things score",
  "phq_value_num_feeling down, depressed, or hopeless score"
)

# 2 & 3. Add columns for presence and manual sum if all 2 items present
result_wide <- result_wide %>%
  mutate(
    phq2_num_items_present = rowSums(!is.na(across(all_of(phq2_items)))),
    phq2_manual_sum = case_when(
      phq2_num_items_present == length(phq2_items) ~ rowSums(across(all_of(phq2_items)), na.rm = FALSE),
      TRUE ~ NA_real_
    )
  )

# 4. Define manual POS/NEG based on sum >=3 (standard cutoff)
result_wide <- result_wide %>%
  mutate(
    phq2_manual_posneg = case_when(
      is.na(phq2_manual_sum) ~ NA_character_,
      phq2_manual_sum >= 3 ~ "Positive",
      phq2_manual_sum < 3 ~ "Negative"
    )
  )

# 5. Presence of recorded total score & pos/neg fields
result_wide <- result_wide %>%
  mutate(
    phq2_total_score_present = !is.na(`phq_value_num_PHQ-2 score`),
    phq2_posneg_recorded = !is.na(`phq_value_CMS PHQ-2 POS/NEG`),
    phq2_posneg_recorded_value = `phq_value_CMS PHQ-2 POS/NEG`
  )

# 6. Frequency counts

freq_summary <- tibble(
  Description = c(
    "PHQ-2 total numeric score present",
    "PHQ-2 numeric items present but no total score",
    "PHQ-2 POS/NEG recorded (any)",
    "PHQ-2 POS/NEG recorded Positive",
    "PHQ-2 POS/NEG recorded Negative",
    "PHQ-2 manual POS/NEG Positive",
    "PHQ-2 manual POS/NEG Negative"
  ),
  Count = c(
    sum(result_wide$phq2_total_score_present, na.rm = TRUE),
    sum(result_wide$phq2_num_items_present == length(phq2_items) & !result_wide$phq2_total_score_present, na.rm = TRUE),
    sum(result_wide$phq2_posneg_recorded, na.rm = TRUE),
    sum(result_wide$phq2_posneg_recorded_value == "Positive", na.rm = TRUE),
    sum(result_wide$phq2_posneg_recorded_value == "Negative", na.rm = TRUE),
    sum(result_wide$phq2_manual_posneg == "Positive", na.rm = TRUE),
    sum(result_wide$phq2_manual_posneg == "Negative", na.rm = TRUE)
  )
)

print(freq_summary)

```
```{r}
result_wide %>%
  mutate(
    manual_phq2_score = rowSums(across(all_of(c(
      "phq_value_num_feeling down, depressed, or hopeless score",
      "phq_value_num_little interest or pleasure in doing things score"
    ))), na.rm = FALSE),
    phq2_score_reported = `phq_value_num_PHQ-2 score`,
    phq9_total_score = `phq_value_num_PHQ-9 Total Score`
  ) %>%
  summarise(
    total_rows = n(),
    manual_phq2_present = sum(!is.na(manual_phq2_score)),
    phq2_reported_present = sum(!is.na(phq2_score_reported)),
    phq9_total_present = sum(!is.na(phq9_total_score)),
    both_manual_and_reported = sum(!is.na(manual_phq2_score) & !is.na(phq2_score_reported)),
    manual_phq2_and_phq9_total = sum(!is.na(manual_phq2_score) & !is.na(phq9_total_score))
  )

```

so this is good, it shows that my manual phq9 sums are working correctly and are aligning with the phq9 total column 
so that is saying for the phq9 values where both manual and automatic sum exist, they are matching, but doesn't say anything about the ones with just the manual phq9

consistency check---
```{r}
phq9_comparison <- result_wide_subset %>%
  filter(!is.na(`phq_value_num_PHQ-9 Total Score`), !is.na(phq9_manual_sum)) %>%
  mutate(score_diff = abs(`phq_value_num_PHQ-9 Total Score` - phq9_manual_sum))

# Summary of differences
summary_stats <- phq9_comparison %>%
  summarise(
    n = n(),
    exact_match = sum(score_diff == 0),
    within_1_point = sum(score_diff <= 1),
    mean_diff = mean(score_diff),
    sd_diff = sd(score_diff)
  )

print(summary_stats)

```
```{r}
result_wide %>%
  filter(!is.na(phq2_manual_posneg) & !is.na(phq2_posneg_recorded_value)) %>%
  summarise(
    total = n(),
    agreement = sum(phq2_manual_posneg == phq2_posneg_recorded_value),
    agreement_pct = mean(phq2_manual_posneg == phq2_posneg_recorded_value) * 100
  )

```
```{r}
library(dplyr)
library(tidyr)

comparison_summary <- result_wide %>%
  mutate(
    manual_phq2_score = rowSums(across(all_of(c(
      "phq_value_num_feeling down, depressed, or hopeless score",
      "phq_value_num_little interest or pleasure in doing things score"
    ))), na.rm = FALSE),

    phq2_score_reported = `phq_value_num_PHQ-2 score`,
    phq9_total_score_reported = `phq_value_num_PHQ-9 Total Score`,
    manual_phq9_score = phq9_manual_sum,

    phq2_posneg_recorded = `phq_value_CMS PHQ-2 POS/NEG`,
    phq9_posneg_recorded = `phq_value_CMS PHQ-9 POS/NEG`
  ) %>%
  summarise(
    total_rows = n(),

    # PHQ-2 comparisons
    phq2_manual_present = sum(!is.na(manual_phq2_score)),
    phq2_reported_present = sum(!is.na(phq2_score_reported)),
    phq2_both_manual_and_reported = sum(!is.na(manual_phq2_score) & !is.na(phq2_score_reported)),
    phq2_only_manual = sum(!is.na(manual_phq2_score) & is.na(phq2_score_reported)),
    phq2_only_reported = sum(is.na(manual_phq2_score) & !is.na(phq2_score_reported)),

    phq2_posneg_present = sum(!is.na(phq2_posneg_recorded)),

    # PHQ-9 comparisons
    phq9_manual_present = sum(!is.na(manual_phq9_score)),
    phq9_reported_present = sum(!is.na(phq9_total_score_reported)),
    phq9_both_manual_and_reported = sum(!is.na(manual_phq9_score) & !is.na(phq9_total_score_reported)),
    phq9_only_manual = sum(!is.na(manual_phq9_score) & is.na(phq9_total_score_reported)),
    phq9_only_reported = sum(is.na(manual_phq9_score) & !is.na(phq9_total_score_reported)),

    phq9_posneg_present = sum(!is.na(phq9_posneg_recorded)),

    phq9_all_items_present = sum(n_items_present == 9, na.rm = TRUE),

    phq2_all_items_present = sum(phq2_num_items_present == 2, na.rm = TRUE)
  ) %>%
  # Convert summary row to long format
  pivot_longer(
    cols = everything(),
    names_to = "metric",
    values_to = "count"
  ) %>%
  # Calculate percentage based on total_rows
  mutate(
    percentage = case_when(
      metric == "total_rows" ~ 100,
      TRUE ~ (count / count[metric == "total_rows"]) * 100
    )
  ) %>%
  select(metric, count, percentage)

print(comparison_summary)

```

so the biggest discrepancy is between the phq2 listed vs manual numeric scores. I want to check to see if the difference is due to some sort of double counting with the phq9s

```{r}
library(dplyr)

# Add flags for presence
phq_overlap <- result_wide %>%
  mutate(
    manual_phq2_present = !is.na(rowSums(across(all_of(c(
      "phq_value_num_feeling down, depressed, or hopeless score",
      "phq_value_num_little interest or pleasure in doing things score"
    ))), na.rm = FALSE)),
    reported_phq2_present = !is.na(`phq_value_num_PHQ-2 score`),
    manual_phq9_present = !is.na(phq9_manual_sum),
    reported_phq9_present = !is.na(`phq_value_num_PHQ-9 Total Score`)
  ) %>%
  summarise(
    total = n(),
    manual_phq2_only = sum(manual_phq2_present & !reported_phq2_present),
    manual_phq2_and_reported_phq2 = sum(manual_phq2_present & reported_phq2_present),
    manual_phq2_and_phq9 = sum(manual_phq2_present & manual_phq9_present),
    manual_phq2_only_no_phq9 = sum(manual_phq2_present & !reported_phq2_present & !manual_phq9_present),
    manual_phq2_only_with_phq9 = sum(manual_phq2_present & !reported_phq2_present & manual_phq9_present)
  )

print(phq_overlap)

```

majority of manual only phq2 scores also have a manual phq ***** come back to this 


Load datasets:
 - demo_data (unique patients)
 - depression_data (PHQ screening)
 - encounters_data (clinical encounters)
  |
  v
Clean MRNs in all datasets (trim, convert to character)
  |
  v
Merge demo_data + depression_data by MRN (mrn_deid)
  |
  v
Convert PHQ screening dates and encounter dates to Date class
  |
  v
Define ±1 month time window around each PHQ screening date
  |
  v
For each encounter date (enc_date):
  - Find PHQ screenings for same MRN
  - Where encounter date falls within ±1 month of PHQ screening date
  (Interval join using foverlaps)
  |
  v
Keep only the PHQ screening **closest in time** to each encounter date
  |
  v
Separate PHQ-2 positive screens:
  - Filter PHQ-2 POS/NEG == "Positive"
  - Define window: PHQ-2 date → PHQ-2 date + 14 days
  |
  v
Filter PHQ-9 Total Scores
  |
  v
Join PHQ-9 scores with PHQ-2 positive screens where PHQ-9 date falls within 14 days after PHQ-2 positive
  (Interval join using foverlaps)
  |
  v
Final dataset:
  - One row per patient encounter
  - With closest PHQ screen date & result
  - PHQ-2 positive screens linked with follow-up PHQ-9 scores (if any)

```{r}

# --- Configuration: Set your data path here ---
# IMPORTANT: Change this path to the folder where you want to save the processed .rds files.
# Using the path from your original script as a default.
data_path <- "Z:/Kucirek/"

# --- Save Intermediate Files ---
# After all the processing, save the key dataframes for fast loading in other scripts.
saveRDS(result_wide, file.path(data_path, "result_wide.rds"))

cat(paste("Intermediate data files saved to:", data_path, "\n"))


```


check uniqueness
so with this data pull all three have different amounts of unique mrns, all from 250,000 to 350,000
```{r}
depression_data_unique <- depression_data %>% distinct(mrn_deid) %>% nrow()
cat("Unique MRNs in depression data:",depression_data_unique, "\n")

demo_data_unique<-demo_data %>% distinct(mrn_deid) %>% nrow()
cat("Unique MRNs in demo data:",demo_data_unique, "\n")

unique_encounters_data<-encounters_data%>% distinct(mrn_deid) %>%nrow()
cat("Unique MRNs in encounters data:", unique_encounters_data, "\n")
```
brief missingness check 
almost nothing is missing this time!
```{r}
library(naniar)
visdat::vis_miss(head(depression_data, 1000))
visdat::vis_miss(head(encounters_data, 1000))
visdat::vis_miss(head(demo_data, 1000))
```